---
title: "Mental health of nurses and doctors in Ukraine during wartime: a nationwide cross-sectional survey"
author: "Vicente Arrona and Roberto Mediavilla"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = FALSE,
                      warning = FALSE,
                      fig.align = "center",
                      fig.width = 20,
                      fig.height = 18) #Directory to save plots
```

```{r envir}
library(tidyverse)
library(gtsummary)
library(tidyr)
library(sjlabelled)
library(here)
library(patchwork)
library(ggh4x)

```

# Prepare information

```{r data}

ds <- readRDS("data/ukr_data.rds")  

cb <- read.csv("ext/data_mapping.csv")

# source("src/viridis_noyellow.R")

variable_labels <- # labels for survey data variables
  
  readxl::read_xlsx("ext/var_labels.xlsx")

source("src/functions.R")
```

## Ukraine conflict singularities

```{r ukr-area-classification}

ua_reg_conflict <- 
  readxl::read_excel("ext/ukr_conflict_reg.xlsx") |>
  mutate(occupation = str_to_title(occupation, locale = "en"),
         combat = str_to_title(combat, locale = "en")) |> 
  mutate(occupation = factor(occupation, levels = c("Yes",
                                                       "Partial",
                                                       "No")),
         combat = factor(combat, levels = c("Yes", "No")),
         loc_3 = as_factor(str_trim(loc_3)),
         loc_en = as_factor(loc_en)
  )

# Add to ds

ds_ua <- 
  ds |>  
  left_join(ua_reg_conflict, by = "loc_3") |> 
  filter(occupation != "Yes")

ds_ua <- 
  ds_ua |> 
  mutate(conflict = if_else(
    occupation == "No" & combat == "No",
    "No conflict zone",
    "Conflict zone"
    ),
    conflict = factor(conflict,
                      levels = c("No conflict zone", 
                                 "Conflict zone"), 
                      ordered = FALSE),
    situation = case_when(
      occupation == "Partial" ~ "Partially occupied",
      combat == "Yes" ~ "Actively in combat",
      TRUE ~ "No conflict area"
    ),
    situation = factor(situation, levels = c("No conflict area",
                                             "Partially occupied",
                                             "Actively in combat"),
                       ordered = FALSE))

```

## Manage variables

```{r label-recode}

ds_ua <- 
  
  ds_ua |> 
  mutate(work_5_rec = fct_collapse(
    work_5,
    "Emergencies" = c("Emergency care outside hospital (e.g., ambulance)",
                      "Emergency department"),
    "In-hospital care" = "Inpatient care (hospital services)",
    "Outpatient care" = c("Primary care (outpatient services)", 
                          "Secondary care (outpatient services)",
                          "Other")),
    work_5_rec = factor(work_5_rec, levels = c("Outpatient care",
                                               "In-hospital care",
                                               "Emergencies"),
                        ordered = FALSE)
    )


ds_ua <- 
  
  ds_ua |> 
  mutate(work_3_rec = fct_collapse(
    work_3,
    "5 years or less" = c("Less than 1 year", "1-3 years", "4-5 years"),
    "More than 10 years" = c("11-20 years", "21-30 years", "31-40 years",
                             "More than 40 years")
  ))


ds_ua <- 
  
  ds_ua |> 
  mutate(scdm_1_rec = fct_collapse(
    scdm_1,
    "20-30" = c("20-25", "26-30"),
    "31-45" = c("31-35", "36-40", "41-45"),
    "46-55" = c("46-50", "51-55"),
    "Over 55" = c("56-60", "61-65", "66-70", "Over 70")
  ))
```

```{r exp-prep}
# EXP Sociodemographic

exp_scdm <- c("scdm_4", "scdm_5", "scdm_6")
exp_scdm_dic <- paste0(exp_scdm, "_dic")

# EXP Occupational

exp_work <- c("work_5", "work_16")
exp_work_dic <- paste0(exp_work, "_dic")

# EXP Violence

exp_vio <- c("work_30", "work_31", "work_32", "work_33")
exp_vio_dic <- paste0(exp_vio, "_dic")

# EXP protective factors

exp_supp <- c("work_21", "work_22", "wb_wami_1", "wb_wami_2")
exp_supp_dic <- paste0(exp_supp, "_dic")

# add to dataset

ds_ua <- 
  
  ds_ua |> 
  
  # recode marital status
  
  mutate(
    scdm_4_dic = fct_collapse(scdm_4,
                              "No partner" = c("Divorced",
                                               "Separated",
                                               "Single",
                                               "Widowed"),
                              "Has a partner" = c("Married",
                                                  "Registered partnership")),
    scdm_4_dic = factor(scdm_4_dic, 
                        levels = c("No partner", "Has a partner"),
                        ordered = FALSE)
  ) |> 
  
  # recode children in household
  
  mutate(
    scdm_5_dic = case_when(
      str_detect(scdm_5, "with children") ~ "Has children",
      str_detect(scdm_5, "without children") ~ "No children",
    TRUE ~ NA),
    scdm_5_dic = factor(scdm_5_dic, 
                        levels = c("Has children", "No children"),
                        ordered = FALSE)
  ) |> 
  
  # recode making ends meet
  
  mutate(
    scdm_6_dic = case_when(
      str_detect(scdm_6, "difficulty") ~ "Difficultly",
      str_detect(scdm_6, "easily") ~ "Easily",
    TRUE ~ NA),
    scdm_6_dic = factor(scdm_6_dic, 
                        levels = c("Difficultly", "Easily"),
                        ordered = FALSE)
  ) |> 
  
  # create dichotomic for contract type
  
  mutate(work_16_dic = fct_recode(work_16,
                                  "Yes" = "Temporary contract",
                                  "No" = "Fixed contract"),
         work_16_dic = factor(work_16_dic,
                              levels = c("Yes", 
                                         "No"),
                              ordered = FALSE)
  ) |> 
  
  # recode violence
  
   mutate(
    across(
      all_of(exp_vio),
      ~ factor(
        fct_collapse(.x,
                     Yes = c("Yes, daily", 
                             "Yes, weekly", 
                             "Yes, monthly", 
                             "Yes, a few times"),
                     No = "No"
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{.col}_dic"
    )
  ) |>
  
  # Recode protocols, drop "Do not know", ensure factor levels
 
   mutate(
     work_29_dic = fct_recode(work_29, 
                              NULL = "Do not know")
    ) |> 

  # relevel protocols

  mutate(
    work_29_dic = fct_relevel(work_29_dic, "No")
    ) |> 
  
  # recode support 
  
  mutate(
    across(
      all_of(c("work_21", "work_22")),
      ~ factor(
        fct_collapse(.x,
                     Yes = c("Always", "Often"),
                     No = c("Sometimes", "Seldom", "Never / Hardly ever")
        ),
        levels = c("Yes", "No"), ordered = FALSE
      ),
      .names = "{col}_dic"
    )
  ) |> 
  
  # recode meaningful career
  
  mutate(
    wb_wami_1_dic = fct_collapse(wb_wami_1,
                                 "Yes" = c("Absolutely true", "Mostly true"),
                                 "No" = c("Absolutely untrue", 
                                          "Mostly untrue"),
                                 NULL = "Neither true nor untrue"),
    wb_wami_1_dic = factor(wb_wami_1_dic, levels = c("Yes", "No"))
  ) |> 
  
  # recode purpose
  
  mutate(
    wb_wami_2_dic = fct_collapse(wb_wami_2,
                                 "Yes" = c("Absolutely true", "Mostly true"),
                                 "No" = c("Absolutely untrue", 
                                          "Mostly untrue"),
                                 NULL = "Neither true nor untrue"),
    wb_wami_2_dic = factor(wb_wami_2_dic, levels = c("Yes", "No"))
  )




outcomes <- c("phq_co", "gad_co", "suic_idea")


# Poisson models need numeric values

ds_ua <- 
  
  ds_ua |> 
  mutate(
    across(
      all_of(outcomes),
      ~ case_when(
        . == "Yes" ~ 1,
        . == "No" ~ 0,
        TRUE ~ NA_real_
      )
    )
  )

exposures <- c("work_21_dic", "work_22_dic",
               "work_30_dic", "work_31_dic", 
               "work_32_dic", "work_33_dic",
               "wb_wami_1_dic", "wb_wami_2_dic")


# Remove observations
ds_ua <- 
  ds_ua |> 
  filter(scdm_1 != "Less than 20 years old") |> 
  mutate(scdm_1 = fct_drop(scdm_1),
         loc_3 = fct_drop(loc_3)) |> 
  mutate(
    across(
      where(is.ordered),
      ~ factor(., ordered = FALSE)
    )
  ) |> 
  mutate(
    across(
      all_of(exposures),
      ~ factor(.x, levels = c("No", "Yes"))
    )
  )



# labels


for (i in 1:nrow(variable_labels)) {
  uuid <- variable_labels$Question_uuid[i]
  label <-  variable_labels$Label[i]
  ds_ua[[uuid]] <- sjlabelled::set_label(ds_ua[[uuid]], label)
}

rm(variable_labels,
   i,
   uuid,
   label)

outcome_order <- c(
  "Depression",
  "Anxiety",
  "Suicide thoughts"
  )

exposure_order <- c(
  "Bullying",
  "Sexual Harassment",
  "Violent threats",
  "Physical violence",
  "Colleague support",
  "Support from superiors",
  "Meaning in work",
  "Purpose in work"
)

adjustment_order <- c(
  "Crude",
  "Partially adjusted",
  "Fully adjusted"
  )

# define covariates and outcomes

outcomes_list <- c("phq_co", "gad_co", "suic_idea")

# for model 2 in each
covars_structural <- c("conflict", "scdm_1_rec", "scdm_2_rec")

# specific

covars_peers <- c("work_5_rec", "work_3_rec")

covars_harbul <- c("work_5_rec", "work_1", "work_3_rec")
  
covars_viol <- c("work_5_rec")

covars_meansup <- c("work_5_rec", "scdm_4_dic", "scdm_5_dic", "work_3_rec")

# assign covariates to each exposure
exposure_map <- list(
  
  "work_21_dic" = covars_peers,
  "work_22_dic" = covars_peers,
  
  "work_30_dic" = covars_harbul,
  "work_33_dic" = covars_harbul,
  
  "work_31_dic" = covars_viol,
  "work_32_dic" = covars_viol,
  
  "wb_wami_1_dic" = covars_meansup,
  "wb_wami_2_dic" = covars_meansup
)
```


# Unweighted tables

```{r scdm-tbl-unw}
scdm_vars <- c("scdm_1_rec", "scdm_4_dic", "scdm_5_dic", "work_1",
               "work_3_rec", "work_5_rec", "conflict")

scdm_tbl <- 
  ds_ua |> 
  select(all_of(scdm_vars), work_2, scdm_2_rec) |> 
  tbl_strata(
    strata = "work_2",
    ~ tbl_summary(
      .,
      by = "scdm_2_rec",
      missing_text = "Missing values"
    ) |> 
      add_overall()
  ) |> 
  as_gt() |> 
  tab_footnote(footnote = "Conflict zones are defined by Proximity to combat areas and occupied territories.")

scdm_tbl

gtsave(scdm_tbl, "out/tables/scdm_tbl_unw.docx")
```

```{r out-by-scdm-unw}
# We calculate the prevalences with confidence intervals
# Good practice because it gives certain information about the sample

# Run for your outcomes
tbl_depression_u <- 
  generate_unweighted_table_out(ds_ua, "phq_co",
                                "Probable Depression")

gtsave(tbl_depression_u, "out/tables/dep_by_scdm_unweighted.docx")

tbl_anxiety_u <- 
  generate_unweighted_table_out(ds_ua, "gad_co", "Probable Anxiety")

gtsave(tbl_anxiety_u, "out/tables/anx_by_scdm_unweighted.docx")

tbl_suic_u <- 
  generate_unweighted_table_out(ds_ua, "suic_idea",
                                "Passive suicide thoughts")

gtsave(tbl_suic_u, "out/tables/suic_by_scdm_unweighted.docx")

# Display
tbl_depression_u
tbl_anxiety_u
tbl_suic_u



```

```{r exp-by-scdm-unw}
# Run function for your outcomes
tbl_harassment_u <- generate_unweighted_table_exp(ds_ua, "work_30_dic", 
                                              "Sexual harassment")
gtsave(tbl_harassment_u, "out/tables/harass_by_scdm_unweighted.docx")

tbl_threats_u <- generate_unweighted_table_exp(ds_ua, "work_31_dic", 
                                           "Violent threats")
gtsave(tbl_threats_u, "out/tables/threats_by_scdm_unweighted.docx")

tbl_violence_u <- generate_unweighted_table_exp(ds_ua, "work_32_dic", 
                                            "Physical violence")
gtsave(tbl_violence_u, "out/tables/violence_by_scdm_unweighted.docx")

tbl_bullying_u <- generate_unweighted_table_exp(ds_ua, "work_33_dic", 
                                            "Bullying")
gtsave(tbl_bullying_u, "out/tables/bullying_by_scdm_unweighted.docx")

tbl_colleagues_u <- generate_unweighted_table_exp(ds_ua, "work_21_dic",
                                              "Colleague support")
gtsave(tbl_colleagues_u, "out/tables/col_supp_by_scdm_unweighted.docx")

tbl_superiors_u <- generate_unweighted_table_exp(ds_ua,"work_22_dic", 
                                         "Support from superiors")
gtsave(tbl_superiors_u, "out/tables/sup_supp_by_scdm_unweighted.docx")
 
tbl_meaning_u <- generate_unweighted_table_exp(ds_ua, "wb_wami_1_dic", 
                                           "Meaning in work")
gtsave(tbl_meaning_u, "out/tables/meaning_by_scdm_unweighted.docx")

tbl_purpose_u <- generate_unweighted_table_exp(ds_ua, "wb_wami_2_dic", 
                                           "Purpose in work")
gtsave(tbl_purpose_u, "out/tables/purpose_by_scdm_unweighted.docx")

# Visualize

tbl_harassment_u
tbl_threats_u
tbl_violence_u
tbl_bullying_u
tbl_colleagues_u
tbl_superiors_u
tbl_meaning_u
tbl_purpose_u
```

```{r exp-prev-unw}

table_all_exposures_u <- gen_exp_tbl_unweighted(ds_ua, exposures)

gtsave(table_all_exposures_u, "out/tables/all_exp_tbl_unweighted.docx")

table_all_exposures_u
```

```{r out-prev-unw}

table_all_outcomes_u <- gen_out_tbl_unweighted(ds_ua, outcomes)

gtsave(table_all_outcomes_u, "out/tables/all_out_tbl_unweighted.docx")

table_all_outcomes_u
```

```{r region-tbl}
reg_tbl <- 
  
  ds_ua |> 
  select(loc_en, work_2, scdm_2_rec) |>
  tbl_strata(
    strata = "work_2",
    ~ tbl_summary(., 
                  by = "scdm_2_rec",
                  label = list(loc_en = "Region")) |> 
      add_overall()
    ) |> 
  as_gt()


reg_tbl
  

gtsave(reg_tbl, "out/tables/tbl_ukr_reg.docx")
```

```{r reg-prev}

vio_exp_agg <- c("work_30_dic", "work_31_dic", "work_32_dic",
                 "work_33_dic")

prot_fac_agg <- c("work_21_dic", "work_22_dic", "wb_wami_1_dic",
                  "wb_wami_2_dic")

out_prev_agg <- c("phq_co", "gad_co", "suic_idea")

exp_reg <-
  
  ds_ua |> 
  group_by(loc_en) |> 
  summarise(
    across(
      all_of(vio_exp_agg),
      ~ mean(. == "Yes", na.rm = TRUE)
    )
  ) |> 
  add_row(tibble_row(loc_en = "Crimea")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_en")

exp_reg
  
saveRDS(exp_reg, "out/dataframes/exposure_regions.rds")
  
out_reg <-
  
  ds_ua |> 
  group_by(loc_en) |> 
  summarise(
    across(
      all_of(out_prev_agg),
      ~ mean(. == 1, na.rm = TRUE)
    )
  ) |> 
  add_row(tibble_row(loc_en = "Crimea"))|> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_en")

out_reg

saveRDS(out_reg, "out/dataframes/outcome_regions.rds")
```

# Bayesian Approach

## Define priors

```{r priors-weak}


get_prior(
  formula = phq_co ~ scdm_1_rec + scdm_2_rec + scdm_4_dic + scdm_5_dic + work_5_rec + work_3_rec + work_1 + work_2 + (1 | loc_3),  # The random effect for region
  data = ds_ua,
  family = poisson(link = "log")
)

# set list of priors.

bin_priors <- c(
  # Intercept MUST be negative
  # Mean -1.5 is ~ 22% prevalence (exp(-1.5))
  # SD 1 allows range from -2.5 to -0.5 (~ 8 to 60%)
  # Prevents model crashing 
  prior(normal(-1.5, 1), class = Intercept),  # vague prior for intercept
  
  # 0.5 allows risk ratios up to ~ 2.7, which is realistic
  prior(normal(0, 0.5), class = b),          # weak prior for predictors
  prior(student_t(3, 0, 1), class = sd)    # weak prior for random effect variance
)



# use stan as backend engine, newer, lighter, faster than default rstan
options(brms.backend = "cmdstanr")
options(mc.cores = 4) # forces it to always run 4 simultaneous cores
```

## Models

### Aggregated

```{r agg-mods}

# define covariates and outcomes

outcomes_list_agg <- c("phq_co", "gad_co")

# for model 2 in each
covars_str_agg <- c("conflict", "scdm_1_rec", "scdm_2_rec", "work_2")

# specific

covars_harbul <- c("work_5_rec", "work_1", "work_3_rec")
  
covars_viol <- c("work_5_rec")

# assign covariates to each exposure
exposure_map_agg <- list(
  
  "work_30_dic" = covars_harbul,
  "work_33_dic" = covars_harbul,
  
  "work_31_dic" = covars_viol,
  "work_32_dic" = covars_viol
)

# Define outcome-exposure binomials for running function
brms_tasks_agg <- expand_grid(
  outcome = outcomes_list_agg,
  exposure = names(exposure_map_agg)
)

# Run
pwalk(
  list(brms_tasks_agg$outcome, brms_tasks_agg$exposure),
  function(out, exp) {
    run_brms_agg(
      outcome = out, 
      exposure = exp, 
      design_df = ds_ua,
      output_dir = "out/bayesian_models_agg"
    )
    }
  )
```

```{r results table bayes agg}
brm_model_names_agg <- ls(pattern = "^bay_", envir = .GlobalEnv)


brm_results_df_agg <- 
  map_dfr(brm_model_names_agg, function(obj_name) {
  
  model <- get(obj_name, envir = .GlobalEnv)
  
  # decode name
  parts <- str_split(obj_name, "_")[[1]]
  
  out_code <- parts[2]
  exp_code <- parts[3]
  prof_code <- parts[4]
  type_code <- parts[5]
  
  # decode elements
  outcome_label <- case_when(
    out_code == "dep"  ~ "Depression",
    out_code == "anx"  ~ "Anxiety"
  )
  
  exposure_label <- case_when(
    exp_code == "har"     ~ "Sexual Harassment",
    exp_code == "bul"     ~ "Bullying",
    exp_code == "threats" ~ "Violent threats",
    exp_code == "viol"    ~ "Physical violence",
    TRUE ~ exp_code
  )
  
  term_lookup <- case_when(
    exp_code == "har"     ~ "work_30_dicYes",
    exp_code == "bul"     ~ "work_33_dicYes",
    exp_code == "threats" ~ "work_31_dicYes",
    exp_code == "viol"    ~ "work_32_dicYes"
  )
  
  
  raw_col_name <- case_when(
    exp_code == "har"     ~ "work_30_dic",
    exp_code == "bul"     ~ "work_33_dic",
    exp_code == "threats" ~ "work_31_dic",
    exp_code == "viol"    ~ "work_32_dic"
  )
  
  
  is_poisson <- model$family$family %in% c("poisson", "binomial")
  
  res <- tidy(
    model,
    effects = "fixed",
    conf.int = TRUE,
    conf.level = 0.95,
    exponentiate = is_poisson
  )
  
  target_row <- 
    res |>
    filter(term == term_lookup)
  
  if(nrow(target_row) > 0) {
    est  <- target_row$estimate[1]
    low  <- target_row$conf.low[1]
    high <- target_row$conf.high[1]
    
    
    
    dat <- model$data
    
    # Check if we can find the columns
    # We look for the raw_col_name we defined above
    if (raw_col_name %in% names(dat)) {
      
      # Extract vectors
      x_vec <- as.numeric(dat[[raw_col_name]])
      # The response is usually the first column in brms data
      y_vec <- as.numeric(dat[[1]]) 
      
      if (is_poisson) {
        # Normalize y to 0/1 if it was imported as 1/2
        if(max(y_vec, na.rm=TRUE) > 1) y_vec <- y_vec - 1
        
        # Calculate Observed Percentages
        # Note: We check for "No" and "Yes" explicitly. 
        # If data is 0/1, change to "0" and "1"
        risk_unexp_val <- mean(y_vec[x_vec == 0], na.rm = TRUE)
        risk_exp_val   <- mean(y_vec[x_vec == 1], na.rm = TRUE)
        
        abs_risk_unexposed <- sprintf("%.1f%%", risk_unexp_val * 100)
        abs_risk_exposed   <- sprintf("%.1f%%", risk_exp_val * 100)
        
      } else {
        # Linear Mean
        mean_unexp_val <- mean(y_vec[x_vec == 0], na.rm = TRUE)
        mean_exp_val   <- mean(y_vec[x_vec == 1], na.rm = TRUE)
        
        abs_risk_unexposed <- sprintf("%.2f", mean_unexp_val)
        abs_risk_exposed   <- sprintf("%.2f", mean_exp_val)
      }
    } else {
      # Debugging: if it still fails, print what columns are actually there
      # warning(paste("Could not find column:", raw_col_name))
      abs_risk_unexposed <- NA
      abs_risk_exposed   <- NA
    }
    
    
    tibble(
      Outcome = outcome_label,
      Exposure = exposure_label,
      Profession = "Overall",
      Est_CI = sprintf("%.2f (%.2f, %.2f)", est, low, high),
      # ADDED: Include the calculated columns here
      Risk_Unexposed = abs_risk_unexposed,
      Risk_Exposed = abs_risk_exposed,
      Rhat = max(rhat(model), na.rm = TRUE)
    )
  } else {
    return(NULL)
  }
})


brm_results_df_agg

saveRDS(brm_results_df_agg, "out/dataframes/brm_results_agg.rds")
writexl::write_xlsx(brm_results_df_agg, "out/dataframes/brm_results_agg.xlsx")

ls() |> 
  str_subset("^bay_") |> 
  rm(list = _)

rm(brms_tasks_agg, brm_model_names_agg, run_brms_agg)
```

## Stratified models

```{r run and save every brms model}

# test
# run_brms_pair(outcome = "phq_co", exposure = "work_21_dic", design_df = ds_ua)
# if it works, then

# Define outcome-exposure binomials for analysis
brms_tasks <- expand_grid(
  outcome = outcomes_list,
  exposure = names(exposure_map)
)

# Run
pwalk(
  list(brms_tasks$outcome, brms_tasks$exposure),
  function(out, exp) {
    run_brms_pair(
      outcome = out, 
      exposure = exp, 
      design_df = ds_ua,
      output_dir = "out/bayesian_models"
    )}
  )
```

# Table of results: Bayesian approach

```{r results table bayes}
brm_model_names <- ls(pattern = "^bay_", envir = .GlobalEnv)


brm_results_df <- 
  map_dfr(brm_model_names, function(obj_name) {
  
  model <- get(obj_name, envir = .GlobalEnv)
  
  # decode name
  parts <- str_split(obj_name, "_")[[1]]
  
  out_code <- parts[2]
  exp_code <- parts[3]
  prof_code <- parts[4]
  type_code <- parts[5]
  
  # decode elements
  outcome_label <- case_when(
    out_code == "dep"  ~ "Depression",
    out_code == "anx"  ~ "Anxiety",
    out_code == "suic" ~ "Suicide thoughts"
  )
  
  exposure_label <- case_when(
    exp_code == "cols"    ~ "Colleague support",
    exp_code == "sup"     ~ "Support from superiors",
    exp_code == "har"     ~ "Harassment",
    exp_code == "bul"     ~ "Bullying",
    exp_code == "threats" ~ "Violent threats",
    exp_code == "viol"    ~ "Physical violence",
    exp_code == "mean"    ~ "Meaning in work",
    exp_code == "purp"    ~ "Purpose in work",
    TRUE ~ exp_code
  )
  
  profession_label <- ifelse(prof_code == "doc",
                             "Doctor",
                             "Nurse")
  
  
  term_lookup <- case_when(
    exp_code == "cols"    ~ "work_21_dicYes",
    exp_code == "sup"     ~ "work_22_dicYes",
    exp_code == "har"     ~ "work_30_dicYes",
    exp_code == "bul"     ~ "work_33_dicYes",
    exp_code == "threats" ~ "work_31_dicYes",
    exp_code == "viol"    ~ "work_32_dicYes",
    exp_code == "mean"    ~ "wb_wami_1_dicYes",
    exp_code == "purp"    ~ "wb_wami_2_dicYes"
  )
  
  
  raw_col_name <- case_when(
    exp_code == "cols"    ~ "work_21_dic",
    exp_code == "sup"     ~ "work_22_dic",
    exp_code == "har"     ~ "work_30_dic",
    exp_code == "bul"     ~ "work_33_dic",
    exp_code == "threats" ~ "work_31_dic",
    exp_code == "viol"    ~ "work_32_dic",
    exp_code == "mean"    ~ "wb_wami_1_dic",
    exp_code == "purp"    ~ "wb_wami_2_dic"
  )
  
  
  model_label <- case_when(
    type_code == "cr" ~ "Crude",
    type_code == "str" ~ "Partially adjusted",
    type_code == "adj" ~ "Fully adjusted"
  )
  
  is_poisson <- model$family$family %in% c("poisson", "binomial")
  
  res <- tidy(
    model,
    effects = "fixed",
    conf.int = TRUE,
    conf.level = 0.95,
    exponentiate = is_poisson
  )
  
  target_row <- 
    res |>
    filter(term == term_lookup)
  
  if(nrow(target_row) > 0) {
    est  <- target_row$estimate[1]
    low  <- target_row$conf.low[1]
    high <- target_row$conf.high[1]
    
    
    
    dat <- model$data
    
    # Check if we can find the columns
    # We look for the raw_col_name we defined above
    if (raw_col_name %in% names(dat)) {
      
      # Extract vectors
      x_raw <- (dat[[raw_col_name]])
      # The response is usually the first column in brms data
      y_vec <- as.numeric(dat[[1]]) 
      
      if (is.factor(x_raw)) {
         x_vec <- as.numeric(x_raw) - 1  # Converts 1/2 to 0/1
      } else {
         x_vec <- as.numeric(as.character(x_raw)) # "Safe" cast
      }
      
      # Double check
      if (min(x_vec, na.rm = TRUE) == 1 && max(x_vec, na.rm = TRUE) == 2) {
          x_vec <- x_vec - 1
      }
      
      if (is_poisson) {
        # Normalize y to 0/1 if it was imported as 1/2
        if(max(y_vec, na.rm=TRUE) > 1) y_vec <- y_vec - 1
        
        # Calculate Observed Percentages
        # Note: We check for "No" and "Yes" explicitly. 
        # If data is 0/1, change to "0" and "1"
        risk_unexp_val <- mean(y_vec[x_vec == 0], na.rm = TRUE)
        risk_exp_val   <- mean(y_vec[x_vec == 1], na.rm = TRUE)
        
        abs_risk_unexposed <- sprintf("%.1f%%", risk_unexp_val * 100)
        abs_risk_exposed   <- sprintf("%.1f%%", risk_exp_val * 100)
        
      } else {
        # Linear Mean
        mean_unexp_val <- mean(y_vec[x_vec == 0], na.rm = TRUE)
        mean_exp_val   <- mean(y_vec[x_vec == 1], na.rm = TRUE)
        
        abs_risk_unexposed <- sprintf("%.2f", mean_unexp_val)
        abs_risk_exposed   <- sprintf("%.2f", mean_exp_val)
      }
    } else {
      # Debugging: if it still fails, print what columns are actually there
      # warning(paste("Could not find column:", raw_col_name))
      abs_risk_unexposed <- NA
      abs_risk_exposed   <- NA
    }
    
    
    tibble(
      Outcome = outcome_label,
      Exposure = exposure_label,
      Profession = profession_label,
      Model = model_label,
      Type = ifelse(is_poisson, "PR", "Beta"),
      Est_CI = sprintf("%.2f (%.2f, %.2f)", est, low, high),
      # ADDED: Include the calculated columns here
      Risk_Unexposed = abs_risk_unexposed,
      Risk_Exposed = abs_risk_exposed,
      Rhat = max(rhat(model), na.rm = TRUE)
    )
  } else {
    
    return(NULL)
  
    }
  })

brm_results_df

# Save
saveRDS(brm_results_df, "out/dataframes/brm_results.rds")
writexl::write_xlsx(brm_results_df, "out/dataframes/brm_results.xlsx")

brm_results_df <- 
  readRDS("out/dataframes/brm_results.rds") |> 
  mutate(Exposure = ifelse(Exposure == "Harassment",
                           "Sexual Harassment", # Naming check
                           Exposure))

# Build table with function
tbl_bay_res <- 
  build_bay_gt(brm_results_df, "PR", 
               "**Bayesian Models**", 
               "Posterior Median PR (95% CrI). Models specified with weakly informative priors: These represent prior beliefs of the estimates. Using them gives more flexibility for the data. All models include Region as a second order covariate.")


tbl_bay_res

gtsave(tbl_bay_res, "out/tables/bay_res_tbl.docx")


ls() |> 
  str_subset("^bay_") |> 
  rm(list = _)

rm(brms_tasks, bin_priors, brm_model_names, run_brms_pair, build_bay_gt)
```

### Sensitivity analyses: Restrictive priors

#### Restrictive priors

```{r priors-restrictive}
# for sensitivity analyses, there is a previous article with GAD-7 and PHQ-9 
# prevalences on physicians: https://doi.org/10.1016/j.psychres.2024.115836

phq_doc_p <- 0.108
intercept_prior_phq <- log(phq_doc_p)

priors_res_phq_doc <- c(
  # informative intercept based on the article, small SD (0.5)
  prior_string(glue("normal({intercept_prior_phq}, 0.5)"), 
               class = "Intercept"),
  
  # restrictive predictors (no PR known)
  # force conservative model, with sd of 0.25, forces data to prove effect
  prior(normal(0, 0.25), class = b),
  
  # weak random effect (standard practice)
  prior(student_t(3, 0, 1), class = sd)
)

gad_doc_p <- 0.165
intercept_prior_gad <- log(gad_doc_p)

priors_res_gad_doc <- c(
  # informative intercept based on the article
  prior_string(glue("normal({intercept_prior_gad}, 0.5)"), 
               class = "Intercept"),
  
  # restrictive predictors (no PR known)
  # force model to be conservative
  prior(normal(0, 0.25), class = b),
  
  # weak random effect (standard practice)
  prior(student_t(3, 0, 1), class = sd)
)
  

# for nursing we do not have information, sorestrict with skeptical betas
# (Vague but mathematically valid for Log-Link)
# Centered on ~13% prevalence, but wide enough to cover 0% to ~50%
priors_sens_nur <- c(
  prior(normal(-2, 1.5), class = Intercept),
  
  # same skepticism to exposure effects
  prior(normal(0, 0.25), class = b),
  
  prior(student_t(3, 0, 1), class = sd)
) 
```

#### Models with restrictive priors

```{r bay-restr-analyses}
# define only phq and gad, is the information we have available
sens_tasks <- expand_grid(
  outcome = c("phq_co", "gad_co"), # restrict here
  exposure = names(exposure_map)
)

# Run
pwalk(
  list(sens_tasks$outcome, sens_tasks$exposure),
  function(out, exp) {
    
    message(glue("\nRunning Sensitivity Analysis for: {out} + {exp}"))
    run_brms_sensitivity(
      outcome = out, 
      exposure = exp, 
      design_df = ds_ua,
      output_dir = "out/bayesian_models_sens" # Saves in new folder
    )
  }
)
```

```{r extract-restr-priors-analysis}
# get files
sens_files <- list.files("out/bayesian_models_sens", 
                         full.names = TRUE)

# extract data
bay_sens_res_df <- map_dfr(sens_files, 
                           function(file_path) {
  
  # parse filename to get metadata
  fname <- str_remove(basename(file_path), ".rds")
  parts <- str_split(fname, "_")[[1]]
  
  # parts[1] = "bay", parts[2] = "sens"
  out_code  <- parts[3]
  exp_code  <- parts[4]
  prof_code <- parts[5]
  type_code <- parts[6] # cr, str, or adj
  
  # We only care about Fully Adjusted for the table
  if (type_code != "adj") return(NULL)
  
  # Decode Labels (Same as before)
  outcome_label <- case_when(
    out_code == "dep" ~ "Depression",
    out_code == "anx" ~ "Anxiety"
  )
  
  exposure_label <- case_when(
    exp_code == "cols"    ~ "Colleague support",
    exp_code == "sup"     ~ "Support from superiors",
    exp_code == "har"     ~ "Sexual Harassment",
    exp_code == "bul"     ~ "Bullying",
    exp_code == "threats" ~ "Violent threats",
    exp_code == "viol"    ~ "Physical violence",
    exp_code == "mean"    ~ "Meaning in work",
    exp_code == "purp"    ~ "Purpose in work"
  )
  
  profession_label <- ifelse(prof_code == "doc", "Doctor", "Nurse")
  
  # Determine Exposure Term
  term_lookup <- case_when(
    exp_code == "cols"    ~ "work_21_dicYes",
    exp_code == "sup"     ~ "work_22_dicYes",
    exp_code == "har"     ~ "work_30_dicYes",
    exp_code == "bul"     ~ "work_33_dicYes",
    exp_code == "threats" ~ "work_31_dicYes",
    exp_code == "viol"    ~ "work_32_dicYes",
    exp_code == "mean"    ~ "wb_wami_1_dicYes",
    exp_code == "purp"    ~ "wb_wami_2_dicYes"
  )
  
  # Load Model
  model <- readRDS(file_path)
  
  # Tidy
  res <- tidy(
    model, 
    effects = "fixed", 
    conf.int = TRUE, 
    conf.level = 0.95, 
    exponentiate = TRUE
    )
  
  target <- res |> filter(term == term_lookup)
  
  if(nrow(target) > 0) {
    est <- target$estimate[1]
    low <- target$conf.low[1]
    high <- target$conf.high[1]
    
    tibble(
      Outcome = outcome_label,
      Exposure = exposure_label,
      Profession = profession_label,
      Analysis = "Sensitivity (Restrictive)", # Mark this row
      Est_CI = sprintf("%.2f (%.2f, %.2f)", est, low, high)
    )
  } else {
    NULL
  }
})

bay_sens_res_df

# Save
writexl::write_xlsx(bay_sens_res_df, "out/dataframes/bay_restr_res.xlsx")
saveRDS(bay_sens_res_df, "out/dataframes/bay_res_sens.rds")
```

```{r merge-bayes-main-and-sens}
bay_results_df <- 
  readRDS("out/dataframes/brm_results.rds") |> 
  mutate(Exposure = case_when(
    Exposure == "Harassment" ~ "Sexual Harassment",
    TRUE ~ Exposure
  ))

# Prepare results, filter full models
main_subset <- 
  
  bay_results_df |>
  filter(Model == "Fully adjusted") |>
  # outcomes studied for sensitivity
  filter(Outcome %in% c("Depression", "Anxiety")) |>
  select(Outcome, Exposure, Profession, Est_CI) |>
  mutate(Analysis = "Main (Weak Priors)")


# load sensitivity df
bay_res_sens_df <- readRDS("out/dataframes/bay_res_sens.rds")


# prepare ds
sens_subset <- 
  
  bay_res_sens_df |>
  select(Outcome, Exposure, Profession, Est_CI, Analysis)

# Merge
bay_comparison_df <- 
  
  bind_rows(main_subset, sens_subset) |> 
  mutate(
    # Extract numbers
    PR = as.numeric(str_extract(Est_CI, "^[0-9\\.]+")),
    Lower = as.numeric(str_extract(Est_CI, "(?<=\\()[0-9\\.]+")),
    Upper = as.numeric(str_extract(Est_CI, "[0-9\\.]+(?=\\))")),
    
    # FIX ORDER: Convert to factor. 
    # We use rev() so "Bullying" appears at the TOP of the plot
    
    Exposure = factor(Exposure, levels = rev(exposure_order))
  )


# table

tbl_sensitivity <- 
  
  bay_comparison_df |>
  select(Outcome, Exposure, Profession, Analysis, Est_CI) |> 
  # Pivot to wide format
  pivot_wider(
    names_from = c(Profession, Analysis),
    values_from = Est_CI,
    names_sep = "_"
  ) |>
  # Order columns logically
  select(Outcome, Exposure, 
         `Doctor_Main (Weak Priors)`, `Doctor_Sensitivity (Restrictive)`,
         `Nurse_Main (Weak Priors)`, `Nurse_Sensitivity (Restrictive)`) |>
  mutate(Outcome = factor(Outcome, levels = c("Depression", "Anxiety")),
         Exposure = factor(Exposure, levels = exposure_order) 
         )|>
  arrange(Outcome, Exposure) |> 
  # Create Table
  gt(
    groupname_col = "Outcome", 
    rowname_col = "Exposure"
    ) |>
  
  # Headers
  tab_header(
    title = md("**Sensitivity Analysis: Restrictive Priors**"),
    subtitle = "Fully Adjusted Prevalence Ratios (95% CrI)"
  ) |>
  
  # Spanners for Profession
  tab_spanner(
    label = md("**Doctor**"),
    columns = starts_with("Doctor")
  ) |>
  tab_spanner(
    label = md("**Nurse**"),
    columns = starts_with("Nurse")
  ) |>
  
  # Clean Column Labels (Remove the "Doctor_" prefix)
  cols_label(
    `Doctor_Main (Weak Priors)` = "Weakly Informative Priors",
    `Doctor_Sensitivity (Restrictive)` = "Restrictive Priors",
    `Nurse_Main (Weak Priors)` = "Weakly Informative Priors",
    `Nurse_Sensitivity (Restrictive)` = "Restrictive Priors"
  ) |>
  
  # Formatting
  cols_align(align = "center", columns = contains("_")) |>
  tab_stub_indent(rows = everything(), indent = 3) |>
  tab_footnote(
    footnote = paste0( "Main Analysis: Weak priors (Normal(-1.5,1)). Restrictive: Doctors use informative intercepts based on prevalence + Skeptical Betas (Normal(0, 0.25)). Nurses use Skeptical Betas. All models include Region as a second-order covariate. Adjusted by Age group, Gender and Proximity to combat areas and occupied territories plus specific covariates:", "\n",
                 "Bullying and sexual harassment adjusted by Healthcare setting, Post-graduate training and Length of service.", "\n",
                 "Violent threats and physical violence adjusted by Healthcare setting.", "\n",
                 "Support from colleagues or superiors adjusted by Healthcare setting and Length of service.", "\n",
                 "Finding meaning or purpose in job adjusted by Healthcare setting, Relationship status, Having children, and Length of service."
  ))

# Save
gtsave(tbl_sensitivity, "out/tables/bayes_sensitivity_comparison.docx")

tbl_sensitivity


#plot

# Create a clean plot
forest_bayes_comp <- 
  
  bay_comparison_df |>
  # extract numeric estimates for plotting
  mutate(
    PR = as.numeric(str_extract(Est_CI, "^[0-9\\.]+")),
    Lower = as.numeric(str_extract(Est_CI, "(?<=\\()[0-9\\.]+")),
    Upper = as.numeric(str_extract(Est_CI, "[0-9\\.]+(?=\\))"))
  ) |>
  mutate(Outcome = factor(Outcome, levels = c("Depression", "Anxiety"))) |> 
  ggplot(aes(x = PR, y = Exposure, shape = Analysis)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_errorbar(aes(xmin = Lower, xmax = Upper), 
                 position = position_dodge(width = 0.5)) +
  facet_wrap(~Profession + Outcome, scales = "free_y") +
  geom_vline(xintercept = 1, linetype = "dashed") +
  scale_x_log10(breaks = c(0.2, 0.5, 1, 2, 4),
                labels = scales::label_number(
                  accuracy = 0.1,
                  decimal.mark = "·"
                )) +
  ggpubr::theme_pubr() + 
  theme(
    legend.text = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    strip.text = element_text(size = 10)
  )

forest_bayes_comp

ggsave(filename = "forest_bayes_comparison.pdf",
       plot = forest_bayes_comp,
       path = "out/plots/",
       width = 210,
       height = 170,
       units = "mm",
       dpi = 320,
       scale = 1.5
       )
```

## Model diagnostics

```{r bayes-diagnostics}
# define file paths for each 
main_files <- list.files("out/bayesian_models",
                         full.names = TRUE,
                         pattern = "\\.rds$")

agg_files <- list.files("out/bayesian_models_agg",
                         full.names = TRUE,
                         pattern = "\\.rds$")

sens_files <- list.files("out/bayesian_models_sens",
                         full.names = TRUE,
                         pattern = "\\.rds$")


# execute
df_main_diag <- process_disk_models(main_files, 
                                    "Weakly Informative Priors")
df_agg_diag <- process_disk_models(agg_files, "Weakly Informative Priors")
df_sens_diag <- process_disk_models(sens_files, "Restrictive Priors")

# Combine and clean
final_diagnostics <- 
  
  bind_rows(df_main_diag, df_agg_diag, df_sens_diag) |> 
  mutate(clean_id = str_remove(model_id, "bay_")) |> 
  mutate(clean_id = str_remove(clean_id, "sens_")) |> 
  separate(
    clean_id,
    into = c("outcome", "exposure", "group", "adjustment"),
    sep = "_",
    extra = "merge"
  ) |> 
  mutate(
    outcome = case_match(outcome,
                         "dep" ~ "Depression",
                         "anx" ~ "Anxiety",
                         "suic" ~ "Suicide thoughts",
                         .default = outcome
                         ),
    exposure = case_match(exposure,
                          "bul" ~ "Bullying",
                          "har" ~ "Sexual Harassment",
                          "threats" ~ "Violent threats",
                          "viol" ~ "Physical violence",
                          "cols" ~ "Colleague support",
                          "sup" ~ "Support from superiors",
                          "mean" ~ "Meaning in work",
                          "purp" ~ "Purpose in work",
                          .default = exposure),
    group = case_match(group,
                       "agg" ~ "Aggregate",
                       "doc" ~ "Doctor",
                       "nur" ~ "Nurse",
                       .default = group),
    adjustment = case_match(adjustment,
                            "cr" ~ "Crude",
                            "str" ~ "Partially adjusted",
                            "adj" ~ "Fully adjusted",
                            .default = adjustment)
    ) |> 
  filter(outcome != "wb") |> 
  select(Type, outcome, exposure, group, adjustment, max_rhat, min_ess_bulk, 
         divergences)


final_diagnostics

# Save
saveRDS(final_diagnostics, "out/dataframes/bayes_diagnostics.rds")
writexl::write_xlsx(final_diagnostics, 
                    "out/dataframes/bayes_diagnostics.xlsx")
```

```{r bayes-diagnostic-plots}
# load 4 models, 2 main and 2 sensitivity, same out x exp, both prof
bay_dep_bul_doc_adj <- 
  readRDS("out/bayes_diagnostic_mods/bay_dep_bul_doc_adj.rds")

bay_dep_bul_nur_adj <- 
  readRDS("out/bayes_diagnostic_mods/bay_dep_bul_nur_adj.rds")

bay_sens_dep_bul_doc_adj <- 
  readRDS("out/bayes_diagnostic_mods/bay_sens_dep_bul_doc_adj.rds")

bay_sens_dep_bul_nur_adj <- 
  readRDS("out/bayes_diagnostic_mods/bay_sens_dep_bul_nur_adj.rds")


# run pipeline
plots_main_doc <- 
  create_diag_plots(bay_dep_bul_doc_adj, 
                    "Doctors (Weakly Informative)",
                    "b_work_33_dicYes")

plots_main_nur <- 
  create_diag_plots(bay_dep_bul_nur_adj, 
                    "Nurses (Weakly Informative)", 
                    "b_work_33_dicYes")

plots_sens_doc <- 
  create_diag_plots(bay_sens_dep_bul_doc_adj, 
                    "Doctors (Restrictive)", 
                    "b_work_33_dicYes")

plots_sens_nur <- 
  create_diag_plots(bay_sens_dep_bul_nur_adj, 
                    "Nurses (Restrictive)",
                    "b_work_33_dicYes")


# grid
final_dx_plots_bayes <- (
  (plots_main_doc$trace + plots_main_doc$ppc) /
  (plots_main_nur$trace + plots_main_nur$ppc) /
  (plots_sens_doc$trace + plots_sens_doc$ppc) /
  (plots_sens_nur$trace + plots_sens_nur$ppc)
  ) + 
  plot_layout(heights = c(1, 1, 1, 1))

# View
final_dx_plots_bayes

ggsave(
  "bayes_diagnostic_plots.pdf",
  plot = final_dx_plots_bayes,
  path = "out/plots/",
  scale = 1.5,
  width = 220,
  height = 160,
  unit = "mm",
  dpi = 350
)

rm(bay_dep_bul_doc_adj, bay_dep_bul_nur_adj, bay_sens_dep_bul_doc_adj,
   bay_sens_dep_bul_nur_adj, final_dx_plots_bayes)
```

```{r bayes-diagnostic-tables}
bayes_dx <- 
  readRDS("out/dataframes/bayes_diagnostics.rds") |> 
  mutate(exposure = if_else(exposure == "purp",
                           "Purpose in work",
                           exposure))

# edit datasets
data_main <- prepare_dx_table_data(bayes_dx, "Weakly Informative Priors")
data_sens <- prepare_dx_table_data(bayes_dx, "Restrictive Priors")


# create table

tbl_main_dx <-
  
  data_main |>
  mutate(outcome = factor(outcome, levels = outcome_order),
         adjustment = factor(adjustment, levels = adjustment_order),
         exposure = factor(exposure, levels = exposure_order)
         ) |>
  arrange(outcome, exposure, adjustment) |>
  # doing this the output in word will look ok
  group_by(outcome, exposure) |> 
  mutate(
    exposure_label = ifelse(row_number() == 1, as.character(exposure), "") 
  ) |> 
  ungroup() |> 
  gt(groupname_col = "outcome") |> 
  cols_move_to_start(columns = c(exposure_label, adjustment)) |> 
  tab_spanner(
    label = "Doctors",
    columns = starts_with("Doc")
    ) |>
  tab_spanner(
    label = "Nurses",
    columns = starts_with("Nur")
    ) |>
  tab_spanner(
    label = "Aggregate",
    columns = starts_with("Agg")
    ) |>
  cols_label(
    exposure_label = "",
    adjustment = "",
    Doctor_max_rhat = "Max R-hat",
    Doctor_min_ess_bulk = "Min ESS",
    Doctor_divergences = "Div.",
    Nurse_max_rhat = "Max R-hat",
    Nurse_min_ess_bulk = "Min ESS",
    Nurse_divergences = "Div.",
    Aggregate_max_rhat = "Max R-hat",
    Aggregate_min_ess_bulk = "Min ESS",
    Aggregate_divergences = "Div.",
    ) |>
  fmt_number(
    columns = ends_with("rhat"),
    decimals = 2
    ) |>
  fmt_integer(
    columns = ends_with("bulk")
    ) |>
  tab_header(
    title = "Bayes' Diagnostics for weakly informative priors"
    ) |>
  tab_options(
    row_group.font.weight = "bold",
    column_labels.font.weight = "bold",
    table.font.size = 10,
    data_row.padding = px(2)
    ) |> 
  tab_footnote(
    locations = cells_column_spanners(spanners = contains("Agg")),
    footnote = "Aggregate models only performed for violence exposures and depression/anxiety."
      ) |> 
  tab_footnote(
    locations = cells_column_labels(columns = contains("rhat")),
    footnote = md("*Gelman-Rubin diagnostic*. Maximum value for R-hat in model estimates, < 1.01 shows good convergence.")
    ) |>
  tab_footnote(
    locations = cells_column_labels(columns = contains("bulk")),
    footnote = md("*Effective Sample Size*. Minimum value for ESS in model estimates. A value > 400 is sufficient for stable estimations.")
    ) |> 
  tab_footnote(
    locations = cells_column_labels(columns = contains("divergences")),
    footnote = md("*Divergences*. No divergences show good model convergence.")
    ) |>
    cols_hide(columns = "exposure")


tbl_main_dx

gtsave(tbl_main_dx, "out/tables/diagnostics_tbl_main_bayes.docx")


tbl_sens_dx <-
  data_sens |>
  mutate(outcome = factor(outcome, levels = outcome_order),
         adjustment = factor(adjustment, levels = adjustment_order),
         exposure = factor(exposure, levels = exposure_order)
         ) |>
  arrange(outcome, exposure, adjustment) |>
  group_by(outcome, exposure) |> 
  mutate(
    exposure_label = ifelse(row_number() == 1, as.character(exposure), "") 
  ) |> 
  ungroup() |> 
  gt(groupname_col = "outcome") |> 
  cols_move_to_start(columns = c(exposure_label, adjustment)) |>  
  tab_spanner(
    label = "Doctors",
    columns = starts_with("Doc")
    ) |>
  tab_spanner(
    label = "Nurses",
    columns = starts_with("Nur")
    ) |>
  cols_label(
    exposure_label = "",
    adjustment = "",
    Doctor_max_rhat = "Max R-hat",
    Doctor_min_ess_bulk = "Min ESS",
    Doctor_divergences = "Div.",
    Nurse_max_rhat = "Max R-hat",
    Nurse_min_ess_bulk = "Min ESS",
    Nurse_divergences = "Div."
    ) |>
  fmt_number(
    columns = ends_with("rhat"),
    decimals = 2
    ) |>
  fmt_integer(
    columns = ends_with("bulk")
    ) |>
  tab_header(
    title = "Bayes' Diagnostics for restrictive priors"
    ) |>
  tab_options(
    row_group.font.weight = "bold",
    column_labels.font.weight = "bold",
    table.font.size = 10,
    data_row.padding = px(2)
    ) |> 
  tab_footnote(
    locations = cells_column_spanners(spanners = contains("Agg")),
    footnote = "Aggregate models only performed for violence exposures and depression/anxiety."
      ) |> 
  tab_footnote(
    locations = cells_column_labels(columns = contains("rhat")),
    footnote = md("*Gelman-Rubin diagnostic*. Maximum value for R-hat in model estimates, < 1.01 shows good convergence.")
    ) |>
  tab_footnote(
    locations = cells_column_labels(columns = contains("bulk")),
    footnote = md("*Effective Sample Size*. Minimum value for ESS in model estimates. A value > 400 is sufficient for stable estimations.")
    ) |> 
  tab_footnote(
    locations = cells_column_labels(columns = contains("divergences")),
    footnote = md("*Divergences*. No divergences show good model convergence.")
    ) |>
    cols_hide(columns = "exposure")

tbl_sens_dx


gtsave(tbl_sens_dx, "out/tables/diagnostics_tbl_sens_bayes.docx")
```

# Survey approach

## Define design

```{r survey design}
ds_ua <- 
  ds_ua |> 
  filter(!is.na(scdm_2_rec))

# As we do not know the absolute numbers but only distributions, we use
# raking for adjusting our sample to the population
# First, define population totals (marginal targets)
pop_profession <- 
  data.frame(
    work_2 = c("Doctor", "Nurse"),
    Freq = c(155725, 243664)
    )

# Calculate margins for gender but with absolute totals
# Female: (155,725 * 0.65) + (243,664 * 0.98) = 339,912
# Male: (155,725 * 0.35) + (243,664 * 0.02) = 59,477

pop_gender <- 
  data.frame(
    scdm_2_rec = c("Female", "Male"),
    Freq = c(339912, 59477)
    )



svy_ua <- 
  svydesign(
    data = ds_ua,
    ids = ~loc_3,  # participants may be more similar within regions
    weights = NULL
    )

# raking is a good practice when applying convenience sampling
svy_ua_w <- rake(
  design = svy_ua,
  sample.margins = list(~work_2, ~scdm_2_rec),
  population.margins = list(pop_profession, pop_gender)
)



rm(pop_profession, pop_gender)
```

## Tables

### Sociodemographic

```{r scdm-tbl-w}
# tbl_svysummary has issues with stratifying, we can only gen information
# on separate columns

# define vars
scdm_vars <- c("scdm_1_rec", "scdm_4_dic", "scdm_5_dic", "work_1", 
               "work_3_rec", "work_5_rec", "conflict")


# We do this first so we can use them in the labels later
n_counts <- 
  ds_ua |> 
  count(work_2, scdm_2_rec)

n_total_counts <- 
  ds_ua |> 
  count(work_2) # For the Overall headers

get_n_style <- 
  function(w, g = NULL) {
    
    if(is.null(g)) {
      
      val <- 
        n_total_counts |> 
        filter(work_2 == w) |> 
        pull(n)
      
      } else {
        
        val <- 
          n_counts |> 
          filter(work_2 == w, 
                 scdm_2_rec == g) |> 
          pull(n)
  }
  style_number(val)
}

# Doctors
n_doc_all <- get_n_style("Doctor")
n_doc_m   <- get_n_style("Doctor", "Male")
n_doc_f   <- get_n_style("Doctor", "Female")

# Nurses
n_nur_all <- get_n_style("Nurse")
n_nur_m   <- get_n_style("Nurse", "Male")
n_nur_f   <- get_n_style("Nurse", "Female")


# Summaries (With add_overall) 

doc_n <- 
  ds_ua |> 
  filter(work_2 == "Doctor") |>
  tbl_summary(
    by = scdm_2_rec,
    include = all_of(scdm_vars),
    statistic = list(all_categorical() ~ "{n}"),
    missing = "no"
  ) |>
  add_overall() |> # Adds stat_0
  modify_header(all_stat_cols() ~ "**{level}** (n)") 

doc_p <- 
  subset(svy_ua_w, work_2 == "Doctor") |>
  tbl_svysummary(
    by = scdm_2_rec,
    include = all_of(scdm_vars),
    statistic = list(all_categorical() ~ "({p}%)"),
    missing = "no"
  ) |>
  add_overall() |> # Adds stat_0
  modify_header(all_stat_cols() ~ "**{level}** (%)")

doc_merged <- 
  tbl_merge(list(doc_n, doc_p), 
            tab_spanner = FALSE)


nur_n <- 
  ds_ua |> 
  filter(work_2 == "Nurse") |>
  tbl_summary(
    by = scdm_2_rec,
    include = all_of(scdm_vars),
    statistic = list(all_categorical() ~ "{n}"),
    missing = "no"
  ) |>
  add_overall() |>
  modify_header(all_stat_cols() ~ "**{level}** (n)")

nur_p <- 
  subset(svy_ua_w, work_2 == "Nurse") |>
  tbl_svysummary(
    by = scdm_2_rec,
    include = all_of(scdm_vars),
    statistic = list(all_categorical() ~ "({p}%)"),
    missing = "no"
  ) |>
  add_overall() |>
  modify_header(all_stat_cols() ~ "**{level}** (%)")

nur_merged <- 
  tbl_merge(list(nur_n, nur_p), 
            tab_spanner = FALSE)


# Merge and GT

scdm_tbl_w <- 
  
  tbl_merge(
    list(doc_merged, nur_merged),
    tab_spanner = c("**Doctor**", "**Nurse**")
  ) |>  
  modify_footnote(everything() ~ NA) |> 
  as_gt() 

# Column merging

# LOGIC:
# stat_0 = Overall
# stat_1 = Female (Alphabetical F < M)
# stat_2 = Male
#
# Suffixes added by tbl_merge:
# _1 = Counts (from the first merge n+p)
# _2 = Props  (from the first merge n+p)
# _1 (outer) = Doctors
# _2 (outer) = Nurses

scdm_tbl_w <- 
  scdm_tbl_w |>

  cols_merge(columns = c("stat_0_1_1", "stat_0_2_1")) |> 
  cols_merge(columns = c("stat_1_1_1", "stat_1_2_1")) |> 
  cols_merge(columns = c("stat_2_1_1", "stat_2_2_1")) |> 
  cols_merge(columns = c("stat_0_1_2", "stat_0_2_2")) |> 
  cols_merge(columns = c("stat_1_1_2", "stat_1_2_2")) |> 
  cols_merge(columns = c("stat_2_1_2", "stat_2_2_2")) |> 
  cols_label(
    stat_0_1_1 = md(glue::glue("**Overall**<br>N = {n_doc_all}")), 
    stat_1_1_1 = md(glue::glue("**Female**<br>N = {n_doc_f}")), 
    stat_2_1_1 = md(glue::glue("**Male**<br>N = {n_doc_m}")),
    stat_0_1_2 = md(glue::glue("**Overall**<br>N = {n_nur_all}")),
    stat_1_1_2 = md(glue::glue("**Female**<br>N = {n_nur_f}")),
    stat_2_1_2 = md(glue::glue("**Male**<br>N = {n_nur_m}"))
  ) |>
  tab_footnote(
    footnote = "n (weighted %)",
    locations = cells_column_labels(
      columns = c(stat_0_1_1, stat_1_1_1, stat_2_1_1, 
                  stat_0_1_2, stat_1_1_2, stat_2_1_2)
    )
  )

# View
scdm_tbl_w

# Save
gtsave(scdm_tbl_w, "out/tables/scdm_tbl_w.docx")

rm(n_counts, n_m_doc, n_m_nur, n_f_doc, n_f_nur, nur_n, nur_p,
   doc_merged, doc_n, doc_p, nur_merged)
```

```{r mh-by-scdm-w}
# Run functions 
tbl_depression_w <- 
  generate_outcome_table_w_out("phq_co", "Probable Depression")
gtsave(tbl_depression_w, "out/tables/dep_by_scdm_w.docx")

tbl_anxiety_w <- 
  generate_outcome_table_w_out("gad_co", "Probable Anxiety")
gtsave(tbl_anxiety_w, "out/tables/anx_by_scdm_w.docx")

tbl_suicide_w <- 
  generate_outcome_table_w_out("suic_idea", "Passive Suicide Thoughts")
gtsave(tbl_suicide_w, "out/tables/suic_by_scdm_w.docx")


tbl_depression_w
tbl_anxiety_w
tbl_suicide_w
```

```{r exp-by-scdm-w}
# Generate tables with function
tbl_harassment_w <- generate_exposure_table_w_exp("work_30_dic", "Sexual harassment")
gtsave(tbl_harassment_w, "out/tables/harass_by_scdm_w.docx")

tbl_threats_w <- generate_exposure_table_w_exp("work_31_dic", "Violent threats")
gtsave(tbl_threats_w, "out/tables/threats_by_scdm_w.docx")

tbl_violence_w <- generate_exposure_table_w_exp("work_32_dic", "Physical violence")
gtsave(tbl_violence_w, "out/tables/violence_by_scdm_w.docx")

tbl_bullying_w <- generate_exposure_table_w_exp("work_33_dic", "Bullying")
gtsave(tbl_bullying_w, "out/tables/bullying_by_scdm_w.docx")

tbl_colleagues_w <- generate_exposure_table_w_exp("work_21_dic", "Colleague support")
gtsave(tbl_colleagues_w, "out/tables/col_supp_by_scdm_w.docx")

tbl_superiors_w <- generate_exposure_table_w_exp("work_22_dic", 
                                         "Support from superiors")
gtsave(tbl_superiors_w, "out/tables/sup_supp_by_scdm_w.docx")

tbl_meaning_w <- generate_exposure_table_w_exp("wb_wami_1_dic", "Meaning in work")
gtsave(tbl_meaning_w, "out/tables/meaning_by_scdm_w.docx")

tbl_purpose_w <- generate_exposure_table_w_exp("wb_wami_2_dic", "Purpose in work")
gtsave(tbl_purpose_w, "out/tables/purpose_by_scdm_w.docx")



# Visualize

tbl_harassment_w
tbl_threats_w
tbl_violence_w
tbl_bullying_w
tbl_colleagues_w
tbl_superiors_w
tbl_meaning_w
tbl_purpose_w


```

### Exposures

```{r exp-overall-w}
# Generate table
table_all_exposures_w <- gen_w_exp_tbl(exposures)

gtsave(table_all_exposures_w, "out/tables/all_exp_tbl_w.docx")

table_all_exposures_w

```

### Outcomes

```{r outcomes-overall-w}
# Generate table
table_all_outcomes_w <- gen_w_out_tbl(outcomes)

gtsave(table_all_outcomes_w, "out/tables/all_out_tbl_w.docx")

table_all_outcomes_w
```

## Svy Models

```{r function to map every model}
# generate the grid for all possible combinations
tasks_grid <- expand_grid(
  outcome = outcomes,
  exposure = names(exposure_map),
  profession = c("Doctor", "Nurse")
)

# run function 
pwalk(
  list(tasks_grid$outcome, 
       tasks_grid$exposure, 
       tasks_grid$profession),
  function(out, exp, prof) {
    message(glue("Running: {out} vs {exp} ({prof})..."))
    run_svy_models(out, exp, prof, svy_ua_w)
  }
)

```

## Survey results table

```{r svy-tbl-res}
# find svy objects
svy_model_names <- ls(pattern = "^svy_", envir = .GlobalEnv)

# Extraction
survey_results_df <- 
  map_dfr(svy_model_names, function(obj_name) {
  
  # Load the model object
  model <- get(obj_name, envir = .GlobalEnv)
  
  # decode filename
  parts <- str_split(obj_name, "_")[[1]]
  
  out_code   <- parts[2]
  exp_code   <- parts[3]
  prof_code  <- parts[4]
  type_code  <- parts[5]
  
  # Decode Labels for the Table
  outcome_label <- case_when(
    out_code == "dep"  ~ "Depression",
    out_code == "anx"  ~ "Anxiety",
    out_code == "suic" ~ "Suicide thoughts"
  )
  
  exposure_label <- case_when(
    exp_code == "cols"    ~ "Colleague support",
    exp_code == "sup"     ~ "Support from superiors",
    exp_code == "har"     ~ "Sexual Harassment",
    exp_code == "bul"     ~ "Bullying",
    exp_code == "threats" ~ "Violent threats",
    exp_code == "viol"    ~ "Physical violence",
    exp_code == "mean"    ~ "Meaning in work",
    exp_code == "purp"    ~ "Purpose in work"
  )
  
  profession_label <- ifelse(prof_code == "doc", "Doctor", "Nurse")
  
  model_label <- case_when(
    type_code == "cr"  ~ "Crude",
    type_code == "str" ~ "Partially",
    type_code == "adj" ~ "Fully Adj."
  )
  
 
  term_lookup <- case_when(
    exp_code == "cols"    ~ "work_21_dicYes",
    exp_code == "sup"     ~ "work_22_dicYes",
    exp_code == "har"     ~ "work_30_dicYes",
    exp_code == "bul"     ~ "work_33_dicYes",
    exp_code == "threats" ~ "work_31_dicYes",
    exp_code == "viol"    ~ "work_32_dicYes",
    exp_code == "mean"    ~ "wb_wami_1_dicYes",
    exp_code == "purp"    ~ "wb_wami_2_dicYes"
  )
  
  # extract stats
  res <- tryCatch({
    
    # Check family
    is_logistic <- model$family$family %in% c("quasipoisson", "binomial")
    
    # Try to tidy
    tidy(model, conf.int = TRUE, exponentiate = is_logistic)
    
  }, error = function(e) {
    # If it fails, print the culprit and return NULL
    warning(paste("FAILED model:", obj_name, "-", e$message))
    return(NULL)
  })
  
  if (is.null(res)) return(NULL)
  
  # exposure term
  target_row <- 
    res |> 
    filter(term == term_lookup)
  
  if(nrow(target_row) > 0) {
    # If multiple rows match (rare), take the first one
    est  <- target_row$estimate[1]
    low  <- target_row$conf.low[1]
    high <- target_row$conf.high[1]
    
    
    # calculate absolute risks/means
    dat <- model$model
    
    exp_var_name <- str_remove(term_lookup, "Yes$")
    resp_var_name <- names(dat)[1]
    
    x_vec <- as.character(dat[[exp_var_name]])
    y_raw <- as.numeric(dat[[resp_var_name]])
    
    if (is.factor(y_raw)) {
       # Ensure it is 0 and 1
       y_vec <- as.numeric(as.character(y_raw)) 
    } else {
       y_vec <- as.numeric(y_raw)
    }
    
    if (is_logistic) {
      # Normalize 1/2 to 0/1 if necessary
      if(max(y_vec, na.rm = TRUE) > 1) y_vec <- y_vec - 1
      
      # Calculate %
      risk_unexp <- mean(y_vec[x_vec == "No"], na.rm = TRUE) * 100
      risk_exp   <- mean(y_vec[x_vec == "Yes"], na.rm = TRUE) * 100
      
      risk_unexp_str <- sprintf("%.1f%%", risk_unexp)
      risk_exp_str   <- sprintf("%.1f%%", risk_exp)
      
      } else {
        
        # Calculate Mean
        mean_unexp <- mean(y_vec[x_vec == "No"], na.rm = TRUE)
        mean_exp   <- mean(y_vec[x_vec == "Yes"], na.rm = TRUE)
        
        risk_unexp_str <- sprintf("%.2f", mean_unexp)
        risk_exp_str   <- sprintf("%.2f", mean_exp)
        }
    
    tibble(
      Outcome = outcome_label,
      Exposure = exposure_label,
      Profession = profession_label,
      Model = model_label,
      Type = ifelse(is_logistic, 
                    "PR", 
                    "Beta"),
      Est_CI = sprintf("%.2f (%.2f, %.2f)", est, low, high),
      Risk_Unexposed = risk_unexp_str,
      Risk_Exposed = risk_exp_str
    )
    
  } else {
    return(NULL)
  }
})


survey_results_df

# Save
saveRDS(survey_results_df, "out/dataframes/svy_results_df.rds")
writexl::write_xlsx(survey_results_df, "out/dataframes/svy_results_df.xlsx")

# generate table
tbl_svy_res <- build_svy_gt(
  survey_results_df, 
  metric_type = "PR", 
  title_text = "**Survey Logistic Models (PR)**", 
  footnote_text = "Weighted Prevalence Ratios (95% CI)"
)


gtsave(tbl_svy_res, "out/tables/svy_res_tbl.docx")


tbl_svy_res

ls() |> 
  str_subset("^svy_") |> 
  rm(list = _)

rm(build_svy_gt, run_svy_models)
```

# Generalized Linear Models with Multilevel variables

## Run models

```{r glm-run-models}
# define covariates
covariate_map <- list(
  "peer" = c("conflict", "scdm_1_rec", "scdm_2_rec", "work_2", "work_5_rec",
             "work_3_rec", "work_1"),
  
  "viol" = c("conflict", "scdm_1_rec", "scdm_2_rec", "work_2", "work_5_rec"),
  
  "har_bul" = c("conflict", "scdm_1_rec", "scdm_2_rec", "work_2", "work_1",
                "work_3_rec", "work_5_rec"),
  
  "meanpur" = c("conflict", "scdm_1_rec", "scdm_2_rec", "work_2",
                "work_5_rec", "work_3_rec", "work_1", "scdm_4_dic",
                "scdm_5_dic"),
  
  "structure" = c("conflict", "scdm_1_rec", "scdm_2_rec", "work_2")
)

analysis_plan <- tribble(
  ~Exposure,     ~Covar_Key,
  "work_21_dic", "peer",
  "work_22_dic", "peer",
  "work_31_dic", "viol",
  "work_32_dic", "viol",
  "work_30_dic", "har_bul",
  "work_33_dic", "har_bul",
  "wb_wami_1_dic", "meanpur",
  "wb_wami_2_dic", "meanpur"
)

outcomes_map <- tribble(
  ~Outcome,    ~Family,
  "phq_co",    "poisson",
  "gad_co",    "poisson",
  "suic_idea",    "poisson",
)

# Define stratification of models
profs <- c("Doctor", "Nurse")

# Generate exposure-outcome binomials
tasks <- expand_grid(
  out_row = outcomes_map,
  exp_row = analysis_plan,
  profession = profs
) |> 
  tidyr::unpack(cols = c(out_row, exp_row))


all_runs_list <- pmap(list(
  tasks$Outcome,
  tasks$Family,
  tasks$Exposure,
  tasks$Covar_Key,
  tasks$profession
), function(outcome, family, exposure, cov_key, prof) {
  
  message(paste("Processing:", outcome, "x", exposure, "in", prof))
  
  res_crude <- run_crude_glm(
    data = ds_ua, 
    outcome_var = outcome,
    exposure_var = exposure, 
    profession = prof,
    cluster_var = "loc_3", 
    family_type = family,
    )

  

  res_str <- run_glm_adj(
    data = ds_ua, 
    outcome_var = outcome, 
    exposure_var = exposure,
    confounder_list = covariate_map[["structure"]], 
    profession = prof,
    cluster_var = "loc_3", 
    family_type = family, 
    model_label = "Partially adjusted"
    )
  
  #look up for specific covariate list
  specific_covars <- covariate_map[[cov_key]]
  
  res_adj <- run_glm_adj(
    data = ds_ua, 
    outcome_var = outcome, 
    exposure_var = exposure,
    confounder_list = specific_covars, 
    profession = prof,
    cluster_var = "loc_3", 
    family_type = family, 
    model_label = "Fully adjusted"
    )
  
  
  # Combine internally
  row_multilevel <- 
    
    bind_rows(
      res_crude$multilevel,
      res_str$multilevel,
      res_adj$multilevel
    )
  
  row_robust <- 
    
    bind_rows(
      res_crude$robust,
      res_str$robust,
      res_adj$robust
    )
  
  # return as clean pair
  return(list(
    multilevel = row_multilevel,
    robust     = row_robust
  ))
})


# Unzip and combine

glm_multilevel_df <- map_dfr(all_runs_list, "multilevel")

glm_robust_df <- map_dfr(all_runs_list, "robust")


# Save

saveRDS(glm_multilevel_df, "out/dataframes/glm_multilevel_df.rds")
writexl::write_xlsx(glm_multilevel_df,
                    "out/dataframes/glm_multilevel_df.xlsx")


saveRDS(glm_robust_df, "out/dataframes/glm_robust_df.rds")
writexl::write_xlsx(glm_robust_df, "out/dataframes/glm_robust_df.xlsx")
```

## GLM results

```{r glm-results}
# SE Ratios
glm_se_ratios <-
  
  glm_multilevel_df |>
  select(Outcome, Exposure, Profession, Adjustment, beta, PR, SE) |> 
  rename(`PR (ML)` = PR,
         `SE (ML)` = SE) |> 
  left_join(glm_robust_df |> 
              select(Outcome, Exposure, Profession, Adjustment, SE),
            by = c("Outcome", "Exposure", "Profession", "Adjustment")) |> 
  rename(`SE (Robust)` = SE) |> 
  mutate(`SE Ratio` = `SE (Robust)` / `SE (ML)`) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_30_dic" ~ "Sexual Harassment",
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "wb_wami_1_dic" ~ "Meaning in work",
      Exposure == "wb_wami_2_dic" ~ "Purpose in work",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co" ~ "Depression",
      Outcome == "gad_co" ~ "Anxiety",
      Outcome == "suic_idea" ~ "Suicide thoughts",
      TRUE ~ Outcome
    )
  )

glm_se_ratios


# Save

saveRDS(glm_se_ratios, "out/dataframes/glm_se_ratios_df.rds")
writexl::write_xlsx(glm_se_ratios, "out/dataframes/glm_se_ratios_df.xlsx")


# Results with ML estimator + SE robust

glm_results <-
  
  glm_multilevel_df |> 
  select(-c(model, N_Analysis, Risk_Unexp, Risk_Exp)) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_30_dic" ~ "Sexual Harassment",
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "wb_wami_1_dic" ~ "Meaning in work",
      Exposure == "wb_wami_2_dic" ~ "Purpose in work",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co" ~ "Depression",
      Outcome == "gad_co" ~ "Anxiety",
      Outcome == "suic_idea" ~ "Suicide thoughts",
      TRUE ~ Outcome
    )
  ) |> 
  mutate(
     Est_CI = sprintf("%.2f (%.2f, %.2f)", PR, CI_l, CI_u)
  )

glm_results

saveRDS(glm_results, "out/dataframes/glm_results_df.rds")
writexl::write_xlsx(glm_results, "out/dataframes/glm_results_df.xlsx")
  

# Load data

glm_results <- readRDS("out/dataframes/glm_results_df.rds")

# Table of results
tbl_binary_glm <- make_stratified_table(
  glm_results,
  "**GLM Multilevel models**",
  "Prevalence Ratio (95% CI). All models include Region as a second-order covariate."
)

tbl_binary_glm


gtsave(tbl_binary_glm, "out/tables/glm_res_tbl.docx")


ls() |> 
  str_subset("^glm_") |> 
  rm(list = _)

rm(glm_se_ratios, make_stratified_table, run_crude_glm, run_glm_adj)
```

# GLM Dose-Response models

```{r glm-sens-dose-resp}

analysis_plan_dose <- tribble(
  ~Exposure,     ~Covar_Key,
  "work_21", "peer",
  "work_22", "peer",
  "work_31", "viol",
  "work_32", "viol",
  "work_30", "har_bul",
  "work_33", "har_bul",
  "wb_wami_1", "meanpur",
  "wb_wami_2", "meanpur",
)

outcomes_map_dose <- tribble(
  ~Outcome,    ~Family,
  "phq_sc",    "gaussian",
  "gad_sc",    "gaussian",
  "mh_phq_9",  "gaussian",
)


# Define exposure-outcome combinations
tasks_dose <- expand_grid(
  out_row = outcomes_map_dose,
  exp_row = analysis_plan_dose,
) |> 
  tidyr::unpack(cols = c(out_row, exp_row))


dose_all <- pmap_dfr(list(
  tasks_dose$Outcome,
  tasks_dose$Family,
  tasks_dose$Exposure,
  tasks_dose$Covar_Key
  ), function(outcome, family, exposure, cov_key) {
  
  message(paste("Processing:", outcome, "&", exposure))

  
  res_adj <- run_glm_dose_emm(
    data = ds_ua,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Fully adjusted"
  ) 
  
  print(res_adj)
})



dose_all <- 
  dose_all |> 
  mutate(
    Est_CI = sprintf("%.2f (%.2f, %.2f)", estimate, conf.low, conf.high),
    Exposure = case_when(
      Exposure == "work_21" ~ "Colleague support",
      Exposure == "work_22" ~ "Support from superiors",
      Exposure == "work_31" ~ "Violent threats",
      Exposure == "work_32" ~ "Physical violence",
      Exposure == "work_30" ~ "Sexual Harassment",
      Exposure == "work_33" ~ "Bullying",
      Exposure == "wb_wami_1" ~ "Meaning in work",
      Exposure == "wb_wami_2" ~ "Purpose in work",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_sc" ~ "PHQ-9 score",
      Outcome == "gad_sc" ~ "GAD-7 score",
      Outcome == "mh_phq_9" ~ "PHQ-9 suicide item score",
      TRUE ~ Outcome
    ),
    Category = if_else(
      Exposure %in% c("Violent threats", "Physical violence",
                      "Sexual Harassment", "Bullying"),
      "Risk factor",
      "Protective factor")
    )

dose_all

saveRDS(dose_all, "out/dataframes/dose_all.rds")
writexl::write_xlsx(dose_all, "out/dataframes/dose_all.xlsx")
```

```{r psw-dose-results}
dose_resp_df <- 
  readRDS("out/dataframes/dose_all.rds") 

# Custom palette: Purple -> Teal -> Green -> Lime
viridis_lime_palette <- c(
  "#440154", # Dark Purple
  "lightblue", # Blue/Teal
  "#35B779", # Medium Green
  "#B4DE2C"  # Lime Green
)

# Assign these colors to labels
custom_colors <- c(
  # Risk Factors 
  "Bullying"                = viridis_lime_palette[1],
  "Sexual Harassment"       = viridis_lime_palette[2],
  "Violent threats"         = viridis_lime_palette[3],
  "Physical violence"       = viridis_lime_palette[4],
  
  # Protective Factors
  "Colleague support"       = viridis_lime_palette[1],
  "Support from superiors"  = viridis_lime_palette[2],
  "Meaning in work"         = viridis_lime_palette[3],
  "Purpose in work"         = viridis_lime_palette[4]
)


dose_plots <-
  
  dose_resp_df |> 
  group_by(Outcome, Exposure) |> 
  mutate(Level_Index = row_number()) |> 
  ungroup() |> 
  mutate(Outcome = factor(Outcome, 
                          levels = c("PHQ-9 score",
                                     "GAD-7 score",
                                     "PHQ-9 suicide item score")),
         Exposure = factor(Exposure, levels = exposure_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = Level_Index, 
             y = estimate, 
             group = Exposure,
             colour = Exposure)) +
  geom_line(linewidth = 0.5,
            position = position_dodge(width = 0.2)) + 
  geom_point(size = 2,
             position = position_dodge(width = 0.2)) + 
  facet_grid(rows = vars(Outcome),
             cols = vars(Category),
             scales = "free",
             switch = "y") + 
  scale_colour_manual(values = custom_colors) +
  scale_x_continuous(breaks = 1:5, minor_breaks = NULL) +
  labs(
    x = "Level of exposure",
    y = "Score change estimate",
    colour ="Exposure"
  ) + 
  facetted_pos_scales(
    y = list(
      Outcome == "PHQ-9 score" ~ scale_y_continuous(
        limits = c(0, 27),
        breaks = c(0, 5, 10, 15, 20, 25)),
      Outcome == "GAD-7 score" ~ scale_y_continuous(
        limits = c(0, 21),
        breaks = c(0, 5, 10, 15, 20)),
      Outcome == 
        "PHQ-9 suicide item score" ~ scale_y_continuous(
        limits = c(0, 4),
        breaks = c(0, 1, 2, 3, 4))
    )
  ) + 
  theme_minimal() +
  theme(
    strip.placement = "outside",  
    strip.text.y.left = element_text(angle = 90, face = "bold", size = 10), 
    strip.text.x = element_text(face = "bold", size = 10),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    panel.border = element_rect(color = "black", fill = NA),  
    axis.title.y = element_blank(), 
    legend.position = "right",
    legend.key.width = unit(1.5, "cm")
  )

dose_plots

ggsave(filename = "dose_resp_plots.pdf",
       plot = dose_plots,
       path = "out/plots/",
       width = 170,
       height = 170,
       units = "mm",
       dpi = 320,
       scale = 1.5
       )

ls() |> 
  str_subset("^glm_") |> 
  rm(list = _)


```

# Absolute risks

```{r abs risks merge}
brm_results_df <- readRDS("out/dataframes/brm_results.rds")

survey_results_df <- readRDS("out/dataframes/svy_results_df.rds")

glm_results_df <- readRDS("out/dataframes/glm_multilevel_df.rds")

# clean
brm_risks <- 
  brm_results_df |> 
  filter(Model == "Fully adjusted") |> 
  select(Outcome, Exposure, Profession, Risk_Unexposed, Risk_Exposed)|>
  rename(Unexposed_Bayesian = Risk_Unexposed,
         Exposed_Bayesian = Risk_Exposed) |> 
  mutate(Exposed_Bayesian = as.numeric(str_replace(Exposed_Bayesian, "%",
                                                   "")),
         Unexposed_Bayesian = as.numeric(str_replace(Unexposed_Bayesian, "%",
                                                   ""))) |> 
  mutate(ARR_Bayesian = abs(Exposed_Bayesian - Unexposed_Bayesian)) |> 
  mutate(Exposure = case_when(
    Exposure == "Harassment" ~ "Sexual Harassment",
    TRUE ~ Exposure
  ))



svy_risks <-
  survey_results_df |> 
  filter(Model == "Fully Adj.") |> 
  select(Outcome, Exposure, Profession, Risk_Unexposed, Risk_Exposed) |> 
  rename(Unexposed_Survey = Risk_Unexposed,
         Exposed_Survey = Risk_Exposed) |> 
  mutate(Exposed_Survey = as.numeric(str_replace(Exposed_Survey, "%",
                                                   "")),
         Unexposed_Survey = as.numeric(str_replace(Unexposed_Survey, "%",
                                                   ""))) |> 
  mutate(ARR_Survey = abs(Exposed_Survey - Unexposed_Survey))


glm_risks <- 
  glm_results_df |> 
  filter(Adjustment == "Fully adjusted") |>
  select(Outcome, Exposure, Profession, Risk_Unexp, Risk_Exp) |> 
  rename(Unexposed_GLM = Risk_Unexp,
         Exposed_GLM = Risk_Exp) |> 
  mutate(Exposed_GLM = as.numeric(str_replace(Exposed_GLM, "%",
                                                   "")),
         Unexposed_GLM = as.numeric(str_replace(Unexposed_GLM, "%",
                                                   ""))) |> 
  mutate(ARR_GLM = abs(Exposed_GLM - Unexposed_GLM)) |> 
   mutate(
    Exposure = case_when(
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_30_dic" ~ "Sexual Harassment",
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "wb_wami_1_dic" ~ "Meaning in work",
      Exposure == "wb_wami_2_dic" ~ "Purpose in work",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co" ~ "Depression",
      Outcome == "gad_co" ~ "Anxiety",
      Outcome == "suic_idea" ~ "Suicide thoughts",
      TRUE ~ Outcome
    )
   )



exposures_risks <-
  brm_risks |> 
  left_join(svy_risks, by = c("Outcome", "Exposure", "Profession")) |> 
  left_join(glm_risks, by = c("Outcome", "Exposure", "Profession"))
  

exposures_risks
```

```{r tbl-arr}

arr_tbl <-

  glm_risks |> 
  pivot_wider(
    names_from = Profession,
    values_from = c("Unexposed_GLM", "Exposed_GLM", "ARR_GLM")
  ) |> 
  mutate(
    across(
      where(is.numeric),
      ~ as.character(paste0(round(.x, 1), "%"))
    )
  ) |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order), 
         Exposure = factor(Exposure, levels = exposure_order)
         ) |>
  arrange(Outcome, Exposure) |> 
  gt(groupname_col = "Outcome",
     rowname_col = "Exposure") |>
  tab_header(title = md("**Absolute prevalence and prevalence difference for each exposure-outcome pair**")) |>
      tab_spanner(
        label = md("**Doctor**"),
        columns = ends_with("Doctor")
      ) |> 
      tab_spanner(
        label = md("**Nurse**"),
        columns = ends_with("Nurse")
      ) |> 
      cols_label(
        starts_with("Unexposed") ~ "Unexposed",
        starts_with("Exposed") ~ "Exposed",
        starts_with("ARR") ~ "Difference"
      ) |> 
      cols_align(
        align = "center",
        columns = contains(c("_Doctor", "_Nurse"))
      ) |> 
      tab_style(
        style = cell_text(align = "left"),
        locations = cells_stub()
        ) |>
      tab_stub_indent(
        rows = everything(), 
        indent = 3
      ) |> 
      tab_footnote(
        locations = cells_column_labels(
          columns = matches("ARR")
        ),
        footnote = md("*Prevalence difference*")
      ) |>
      tab_footnote(footnote = "Estimates from fully adjusted multilevel models.")


arr_tbl

gtsave(arr_tbl, "out/dataframes/arr_table_long.docx")

```

# Sensitivity forest plot

```{r sens forest}
brm_res <- readRDS("out/dataframes/brm_results.rds") |> 
  filter(Type == "PR", Model == "Fully adjusted") |> 
  select(Outcome, Exposure, Profession, Est_CI) |> 
  mutate(Analysis = "Bayesian main (Weakly informative priors)")


brm_sens <- readRDS("out/dataframes/bay_res_sens.rds") |> 
  mutate(
    Analysis = "Bayesian sensitivity (Restrictive priors)")
  

svy_res <- readRDS("out/dataframes/svy_results_df.rds") |> 
  filter(Type == "PR", Model == "Fully Adj.") |> 
  select(-c(Model, Type), -contains("Risk_")) |> 
  mutate(Analysis = "Survey design regression")

glm_res <- readRDS("out/dataframes/glm_results_df.rds") |> 
  filter(Adjustment == "Fully adjusted") |>
  select(Outcome, Exposure, Profession, Est_CI) |> 
  mutate(Analysis = "GLM")


sens_df <-
  brm_res |> 
  bind_rows(brm_sens, svy_res, glm_res) |> 
  mutate(Outcome = case_when(
    str_detect(Outcome, "Ideation") ~ "Suicide thoughts",
    TRUE ~ Outcome),
    Exposure = if_else(Exposure == "Harassment", 
                       "Sexual Harassment",
                       Exposure))
  
sens_df

forest_sens_comp <-
  
  sens_df |>
    filter(Outcome != "Suicide thoughts") |> 
  # extract numeric estimates for plotting
  mutate(
    PR = as.numeric(str_extract(Est_CI, "^[0-9\\.]+")),
    Lower = as.numeric(str_extract(Est_CI, "(?<=\\()[0-9\\.]+")),
    Upper = as.numeric(str_extract(Est_CI, "[0-9\\.]+(?=\\))"))
  ) |>
  mutate(Outcome = factor(Outcome, levels = c("Depression", "Anxiety")),
         Exposure = factor(Exposure, levels = rev(exposure_order)),
         Analysis = factor(
           Analysis,
           levels = c("GLM",
                      "Survey design regression",
                      "Bayesian main (Weakly informative priors)",
                      "Bayesian sensitivity (Restrictive priors)"))) |>
  arrange(Outcome, Exposure, Analysis) |> 
  ggplot(aes(x = PR, 
             y = Exposure, 
             shape = Analysis)) +
  geom_point(position = position_dodge(width = 0.5), 
             size = 3) +
  geom_errorbar(aes(xmin = Lower, 
                    xmax = Upper), 
                 position = position_dodge(width = 0.5)) +
  facet_wrap(~Profession + Outcome, 
             scales = "free_y") +
  geom_vline(xintercept = 1, 
             linetype = "dashed") +
  scale_x_log10(breaks = c(0.2, 0.5, 1, 2, 4), 
                labels = scales::label_number(
                  accuracy = 0.1,
                  decimal.mark = "·"
                )) +
  theme(
    legend.text = element_text(size = 10),
    legend.margin = margin(b = -5), # pulls legend close to plot
    plot.margin = margin(0, 0.1, 0, 0, "cm"),
    panel.spacing.x = unit(0.5, "cm"),
    strip.text = element_text(size = 10),
    axis.title.x = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  ) +
  ggpubr::theme_pubr()


forest_sens_comp

ggsave(filename = "forest_sens_comparison.pdf",
       plot = forest_sens_comp,
       path = "out/plots/",
       width = 210,
       height = 170,
       units = "mm",
       dpi = 320,
       scale = 2.2
       )


forest_sens_suic <-
  
  sens_df |>
    filter(Outcome == "Suicide thoughts") |> 
  # extract numeric estimates for plotting
  mutate(
    PR = as.numeric(str_extract(Est_CI, "^[0-9\\.]+")),
    Lower = as.numeric(str_extract(Est_CI, "(?<=\\()[0-9\\.]+")),
    Upper = as.numeric(str_extract(Est_CI, "[0-9\\.]+(?=\\))"))
  ) |> 
    mutate(Exposure = factor(Exposure, levels = rev(exposure_order)),
           Analysis = factor(
             Analysis,
             levels = c("GLM",
                        "Survey design regression",
                        "Bayesian main (Weakly informative priors)",
                        "Bayesian sensitivity (Restrictive priors)"))) |> 
  ggplot(aes(x = PR, 
             y = Exposure,
             shape = Analysis)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_errorbar(aes(xmin = Lower, xmax = Upper), 
                 position = position_dodge(width = 0.5)) +
  facet_wrap(~Profession + Outcome, scales = "free_y") +
  geom_vline(xintercept = 1, linetype = "dashed") +
  scale_x_log10(breaks = c(0.2, 0.5, 1, 2, 4), 
                labels = scales::label_number(
                  accuracy = 0.1,
                  decimal.mark = "·"
                )) +
  theme(
    legend.text = element_text(size = 10),
    legend.margin = margin(b = -5), # pulls legend close to plot
    plot.margin = margin(0, 0.1, 0, 0, "cm"),
    panel.spacing.x = unit(0.5, "cm"),
    strip.text = element_text(size = 10),
    axis.title.x = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  ) +
  ggpubr::theme_pubr() 

forest_sens_suic

ggsave(filename = "forest_sens_comparison_suic.pdf",
       plot = forest_sens_suic,
       path = "out/plots/",
       width = 210,
       height = 170,
       units = "mm",
       dpi = 320,
       scale = 1.5
       )
```

# Sensitivity table

```{r sens tbl}

tbl_sensitivity_all <-
  
  sens_df |>
  select(Outcome, Exposure, Profession, Analysis, Est_CI) |> 
  # Pivot to wide format
  pivot_wider(
    names_from = c(Profession, Analysis),
    values_from = Est_CI,
    names_sep = "_"
  ) |>
  # Order columns logically
  select(Outcome, Exposure, 
         contains("Doctor_GLM"), contains("Doctor_Survey"),  
         contains("Doctor_Bayesian main"), contains("Doctor_Bayesian sens"), 
         contains("Nurse_GLM"), contains("Nurse_Survey"),
         contains("Nurse_Bayesian main"), contains("Nurse_Bayesian sens") 
         ) |>
  mutate(Outcome = factor(Outcome, levels = outcome_order), 
         Exposure = factor(Exposure, levels = exposure_order)) |>
  arrange(Outcome, Exposure) |> 
  # Create Table
  gt(groupname_col = "Outcome", rowname_col = "Exposure") |>
  
  # Headers
  tab_header(
    title = md("**Sensitivity Analysis: All methods**"),
    subtitle = "Fully Adjusted Prevalence Ratios (95% CI or CrI)"
  ) |>
  
  # Spanners for Profession
  tab_spanner(
    label = md("**Doctor**"),
    columns = starts_with("Doctor")
  ) |>
  tab_spanner(
    label = md("**Nurse**"),
    columns = starts_with("Nurse")
  ) |>
  
  # Clean Column Labels (Remove the "Doctor_" prefix)
  cols_label(
    `Doctor_Bayesian main (Weakly informative priors)` = 
      "Bayesian (Weak priors)",
    `Doctor_Bayesian sensitivity (Restrictive priors)` = 
      "Bayesian (Restrictive)",
    `Doctor_Survey design regression` = "Survey design",
    `Doctor_GLM` = "GLM Multilevel",
    `Nurse_Bayesian main (Weakly informative priors)` = 
      "Bayesian (Weak priors)",
    `Nurse_Bayesian sensitivity (Restrictive priors)` = 
      "Bayesian (Restrictive)",
    `Nurse_Survey design regression` = "Survey design",
    `Nurse_GLM` = "GLM Multilevel",
  ) |>
  
  # Formatting
  cols_align(align = "center", columns = contains("_")) |>
  tab_stub_indent(rows = everything(), indent = 3) |>
  tab_footnote(
    footnote = "Fully adjusted models."
  ) |> 
  tab_footnote(
    footnote = "Multilevel GLM.",
    locations = cells_column_labels(columns = contains("GLM"))
  ) |> 
  tab_footnote(
    footnote ="Survey design applied with multivariate regression.",
    locations = cells_column_labels(columns = contains("Survey"))
  ) |> 
  tab_footnote(
    footnote =  "Bayesian Restrictive: Doctors use informative intercepts based on prevalence (Anxiety and depression, no information on suicide thoughts) + Skeptical Betas; Nurses use Skeptical Betas. ",
    locations = cells_column_labels(columns = contains("Restrictive"))
  )

tbl_sensitivity_all

# Save
gtsave(tbl_sensitivity_all, "out/tables/sensitivity_comparison_all.docx")
```

# Maps

## Aggregated prevalences

### Exposures and Outcomes

```{r map generation-prev}
darkblue = "#0045A8"
aqua = "#38aec5"
cyan = "#00C4D6"



# IMPORTANT:
# First time running this code, installation needs to be like this:


# install.packages(
#   "rnaturalearthhires",
#   repos = "https://ropensci.r-universe.dev",
#   type = "source"
# )


ukraine <- rnaturalearth::ne_states(country = "ukraine", 
                                  returnclass = "sf")

# crimea is included as russia (wrong)
crimea <- 
  rnaturalearth::ne_states(country = "russia",
                                   returnclass = "sf") |> 
  filter(name == "Crimea") |> 
  select(fips, geometry)



# get data
exp_reg <- readRDS("out/dataframes/exposure_regions.rds") |> 
  pivot_longer(
    cols = starts_with("work_"),
    names_to = "Exposure",
    values_to = "Prevalence"
  ) |> 
  mutate(Exposure = case_when(
    Exposure == "work_30_dic" ~ "Sexual Harassment",
    Exposure == "work_31_dic" ~ "Violent threats",
    Exposure == "work_32_dic" ~ "Physical violence",
    Exposure == "work_33_dic" ~ "Bullying",
  ))

out_prev_agg <- c("phq_co", "gad_co", "suic_idea")

out_reg <- readRDS("out/dataframes/outcome_regions.rds") |> 
  pivot_longer(
    cols = all_of(out_prev_agg),
    names_to = "Outcome",
    values_to = "Prevalence"
  ) |> 
  mutate(Outcome = case_when(
    Outcome == "phq_co" ~ "Depression",
    Outcome == "gad_co" ~ "Anxiety",
    Outcome == "suic_idea" ~ "Suicide thoughts",
  ))


# join with geometry data
map_info_prev_exp <- 
  ukraine |>
  select(fips, geometry) |>   
  bind_rows(crimea) |> 
  rename(fips_code = fips) |>        
  inner_join(exp_reg, by = "fips_code")

map_info_prev_exp

map_info_prev_out <- 
  ukraine |>
  select(fips, geometry) |>   
  bind_rows(crimea) |> 
  rename(fips_code = fips) |>        
  inner_join(out_reg, by = "fips_code")

map_info_prev_out

# maps
#outcomes

outcomes_gen_map <-
  
  map_info_prev_out |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |>
  arrange(Outcome) |> 
  ggplot() +
  geom_sf(aes(fill = Prevalence), color = "white", size = 0.2) +  
  scale_fill_gradient(low = "#dae6f2",
                      high = darkblue,
                      na.value = "turquoise1",
                      labels = scales::percent,
                      limits = c(0, 0.5)) +
  geom_sf_text(
    aes(
      label = ifelse(
        is.na(Prevalence),
        "ND",
        scales::percent(Prevalence, accuracy = 1)
        )
      ),
    size = 3,
    check_overlap = TRUE
    ) +
  scale_color_manual(values = c("black", "white"), guide = "none") +
  facet_wrap(~Outcome, ncol = 2) +
  labs(
    fill = "Prevalence") +
  ggpubr::theme_pubr() +
  theme(
    legend.position = "right",
    legend.text = element_text(size = 10),
    axis.title = element_blank(), 
    axis.text = element_blank(),  
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    strip.text = element_text(size = 10, face = "bold"),
  ) 

outcomes_gen_map


ggsave(
  "outcomes_map.pdf",
  plot = outcomes_gen_map,
  path = "out/",
  scale = 1.7,
  width = 210,
  height = 160,
  unit = "mm",
  dpi = 350
)


# exposures

exposures_gen_map <-
  map_info_prev_exp |> 
  mutate(Exposure = factor(Exposure, levels = exposure_order)) |> 
  arrange(Exposure) |> 
  ggplot() +
  geom_sf(aes(fill = Prevalence), color = "white", size = 0.2) +  
  scale_fill_gradient(low = "#dae6f2",
                      high = darkblue,
                      na.value = "turquoise1",
                      labels = scales::percent,
                      limits = c(0, 0.5)) +
  geom_sf_text(
    aes(
      label = ifelse(
        is.na(Prevalence),
        "ND",
        scales::percent(Prevalence, accuracy = 1)
        )
      ),
    size = 3,
    check_overlap = TRUE
    ) +
  scale_color_manual(values = c("black", "white"), guide = "none") +
  facet_wrap(~Exposure, ncol = 2) +
  labs(
    fill = "Prevalence") +
  ggpubr::theme_pubr() +
  theme(
    legend.position = "right",
    legend.text = element_text(size = 10),
    axis.title = element_blank(), 
    axis.text = element_blank(),  
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    strip.text = element_text(size = 10, face = "bold"),
  ) 

exposures_gen_map

ggsave(
  "exposures_map.pdf",
  plot = exposures_gen_map,
  path = "out/",
  scale = 1.7,
  width = 210,
  height = 160,
  unit = "mm",
  dpi = 350
)
```

## Aggregated ARs

### Depression

```{r reg-dep-maps-prep}

# effect of violence on dep
# depression
bay_dep_har_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_dep_har_agg_adj.rds")

bay_dep_bul_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_dep_bul_agg_adj.rds")

bay_dep_threats_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_dep_threats_agg_adj.rds")

bay_dep_viol_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_dep_viol_agg_adj.rds")

reg_dep_har <- 
  
  bay_dep_har_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_30_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_30_dicYes
    ) |>
  mutate(
    prob_dep_har_No = plogis(region_log_No),
    prob_dep_har_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_Har_dep = mean(prob_dep_har_No),
    Yes_Har_dep = mean(prob_dep_har_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " ")) |>
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("Har_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Sexual Harassment",
    Outcome = "Depression"
  ) |> 
  select(-loc_3)



reg_dep_bul <- 
  
  bay_dep_bul_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_33_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_33_dicYes
    ) |>
  mutate(
    prob_dep_bul_No = plogis(region_log_No),
    prob_dep_bul_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_bul_dep = mean(prob_dep_bul_No),
    Yes_bul_dep = mean(prob_dep_bul_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " ")) |> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("bul_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Bullying",
    Outcome = "Depression"
  ) |> 
  select(-loc_3)



reg_dep_threats <- 
  
  bay_dep_threats_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_31_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_31_dicYes
    ) |>
  mutate(
    prob_dep_threats_No = plogis(region_log_No),
    prob_dep_threats_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_threats_dep = mean(prob_dep_threats_No),
    Yes_threats_dep = mean(prob_dep_threats_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " "))|> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("threats_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Violent threats",
    Outcome = "Depression"
  ) |> 
  select(-loc_3)




reg_dep_viol <- 
  
  bay_dep_viol_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_32_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_32_dicYes
    ) |>
  mutate(
    prob_dep_viol_No = plogis(region_log_No),
    prob_dep_viol_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_viol_dep = mean(prob_dep_viol_No),
    Yes_viol_dep = mean(prob_dep_viol_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " "))|> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("viol_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Physical violence",
    Outcome = "Depression"
  ) |> 
  select(-loc_3)




# join all
reg_dep_exp <- 
  
  reg_dep_har |> 
  select(loc_en, fips_code, Outcome, Exposure, Category, Probability) |> 
  bind_rows(reg_dep_bul, reg_dep_threats, reg_dep_viol)


reg_dep_exp


saveRDS(reg_dep_exp, "out/dataframes/region_depression_assoc.rds")
writexl::write_xlsx(reg_dep_exp,
                    "out/dataframes/region_depression_assoc.xlsx")
```

### Anxiety

```{r reg-anx-maps-prep}
bay_anx_har_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_anx_har_agg_adj.rds")

bay_anx_bul_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_anx_bul_agg_adj.rds")

bay_anx_threats_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_anx_threats_agg_adj.rds")

bay_anx_viol_agg_adj <-
  readRDS("out/bayesian_models_agg/bay_anx_viol_agg_adj.rds")


# effect of violence on dep
# anxiety
reg_anx_har <- 
  
  bay_anx_har_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_30_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_30_dicYes
    ) |>
  mutate(
    prob_anx_har_No = plogis(region_log_No),
    prob_anx_har_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_Har_anx = mean(prob_anx_har_No),
    Yes_Har_anx = mean(prob_anx_har_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " "))|> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("Har_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Sexual Harassment",
    Outcome = "Anxiety"
  ) |> 
  select(-loc_3)



reg_anx_bul <- 
  
  bay_anx_bul_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_33_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_33_dicYes
    ) |>
  mutate(
    prob_anx_bul_No = plogis(region_log_No),
    prob_anx_bul_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_bul_anx = mean(prob_anx_bul_No),
    Yes_bul_anx = mean(prob_anx_bul_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " "))|> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("bul_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Bullying",
    Outcome = "Anxiety"
  ) |> 
  select(-loc_3)



reg_anx_threats <- 
  
  bay_anx_threats_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_31_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_31_dicYes
    ) |>
  mutate(
    prob_anx_threats_No = plogis(region_log_No),
    prob_anx_threats_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_threats_anx = mean(prob_anx_threats_No),
    Yes_threats_anx = mean(prob_anx_threats_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " "))|> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("threats_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Violent threats",
    Outcome = "Anxiety"
  ) |> 
  select(-loc_3)




reg_anx_viol <- 
  
  bay_anx_viol_agg_adj |> 
  spread_draws(
    b_Intercept, b_work_32_dicYes, r_loc_3[loc_3, term]
    ) |> 
  mutate(
    region_log_No = b_Intercept + r_loc_3,
    region_log_Yes = b_Intercept + r_loc_3 + b_work_32_dicYes
    ) |>
  mutate(
    prob_anx_viol_No = plogis(region_log_No),
    prob_anx_viol_Yes = plogis(region_log_Yes)
    ) |> 
  group_by(loc_3) |> 
  summarise(
    No_viol_anx = mean(prob_anx_viol_No),
    Yes_viol_anx = mean(prob_anx_viol_Yes)
    ) |> 
  mutate(loc_3 = str_replace_all(loc_3, "\\.", " ")) |> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  mutate(loc_3 = case_when(
           loc_3 == "М  Київ" ~ "М. Київ",
           TRUE ~ loc_3
         )) |> 
  add_row(tibble_row(loc_3 = "Ар Крим")) |> 
  left_join(ua_reg_conflict |> select(loc_3, loc_en, fips_code),
            by = "loc_3") |> 
  pivot_longer(
    cols = contains("viol_"),
    names_to = "Category",
    values_to = "Probability"
  ) |> 
  mutate(
    Category = case_when(
      str_detect(Category, "No") ~ "No",
      str_detect(Category, "Yes") ~ "Yes"
    ),
    Exposure = "Physical violence",
    Outcome = "Anxiety"
  ) |> 
  select(-loc_3)




# join all
reg_anx_exp <- 
  
  reg_anx_har |> 
  select(loc_en, fips_code, Outcome, Exposure, Category, Probability) |> 
  bind_rows(reg_anx_bul, reg_anx_threats, reg_anx_viol)



reg_anx_exp



saveRDS(reg_anx_exp, "out/dataframes/region_anxiety_assoc.rds")
writexl::write_xlsx(reg_anx_exp, "out/dataframes/region_anxiety_assoc.xlsx")
```

### Maps

```{r map generation-assoc}

reg_dep_exp <- readRDS("out/dataframes/region_depression_assoc.rds")
reg_anx_exp <- readRDS("out/dataframes/region_anxiety_assoc.rds")


map_data <- 
  reg_dep_exp |>
  bind_rows(reg_anx_exp)


darkblue = "#0045A8"
aqua = "#38aec5"
cyan = "#00C4D6"

ukraine <- rnaturalearth::ne_states(country = "ukraine", 
                                  returnclass = "sf")

# crimea is included as russia (wrong)
crimea <- 
  rnaturalearth::ne_states(country = "russia",
                                   returnclass = "sf") |> 
  filter(name == "Crimea") |> 
  select(fips, geometry)

map_info_assoc <- 
  ukraine |>
  select(fips, geometry) |>   
  bind_rows(crimea) |> 
  rename(fips_code = fips) |>        
  left_join(map_data, by = "fips_code")


map_info_assoc


# depression

dep_assoc_map_grid <-
  
  map_info_assoc |> 
  filter(Outcome == "Depression") |> 
  mutate(Exposure = factor(Exposure, levels = exposure_order)) |>
  arrange(Exposure) |>
  ggplot() +
  geom_sf(aes(fill = Probability),
          color = "white",
          size = 0.2) +
  scale_fill_gradient(low = "#dae6f2",
                      high = darkblue,
                      na.value = "turquoise1",
                      labels = scales::percent,
                      limits = c(0.1, 0.6)) +
  geom_sf_text(
    aes(
      label = ifelse(
        is.na(Probability),
        "ND",
        scales::percent(Probability, accuracy = 1)
        ),
      color = Probability > 0.6
      ),
    size = 2.5,
    check_overlap = FALSE
    ) +
  coord_sf(expand = FALSE) + # removes internal padding between map and box
  scale_color_manual(values = c("black", "white"), guide = "none") +
  facet_grid(rows = vars(Exposure),
             cols = vars(Category)) +
  labs(fill = "Absolute risk") +
  ggpubr::theme_pubr() +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
    panel.spacing = unit(0.2, "lines"),
    legend.position = "right",
    legend.box.margin = margin(0, 0, 0, 0),
    legend.margin = margin(0, 0, 0, 0),
    legend.text = element_text(size = 10),
    plot.title = element_text(hjust = 0.5),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    strip.text = element_text(size = 10, face = "bold")
    ) 


dep_assoc_map_grid

ggsave(
  "assoc_dep_map.pdf",
  plot = dep_assoc_map_grid,
  path = "out/",
  scale = 1.7,
  width = 210,
  height = 160,
  unit = "mm",
  dpi = 350
)

# anxiety


anx_assoc_map_grid <-
  map_info_assoc |> 
  filter(Outcome == "Anxiety") |> 
  mutate(Exposure = factor(Exposure, levels = exposure_order)) |>
  arrange(Exposure) |>
  ggplot() +
  geom_sf(aes(fill = Probability),
          color = "white",
          size = 0.2) +
  scale_fill_gradient(low = "#dae6f2",
                      high = darkblue,
                      na.value = "turquoise1",
                      labels = scales::percent,
                      limits = c(0.1, 0.6)) +
  geom_sf_text(
    aes(
      label = ifelse(
        is.na(Probability),
        "ND",
        scales::percent(Probability, accuracy = 1)
        )
      ),
    size = 2.5,
    check_overlap = FALSE
    ) +
  coord_sf(expand = FALSE) +
  scale_color_manual(values = c("black", "white"), guide = "none") +
  facet_grid(rows = vars(Exposure),
             cols = vars(Category)) +
  labs(
    fill = "Absolute risk") +
  ggpubr::theme_pubr() +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
    panel.spacing = unit(0.2, "lines"),
    legend.position = "right",
    legend.box.margin = margin(0, 0, 0, 0),
    legend.margin = margin(0, 0, 0, 0),
    legend.text = element_text(size = 10),
    plot.title = element_text(hjust = 0.5),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    strip.text = element_text(size = 10, face = "bold")
    ) 
    
anx_assoc_map_grid

ggsave(
  "assoc_anx_map.pdf",
  plot = anx_assoc_map_grid,
  path = "out/",
  scale = 1.7,
  width = 210,
  height = 160,
  unit = "mm",
  dpi = 350
)

```

# Cronbach's Alpha

```{r cronbachs-alpha}
phq_items <- 
  ds_ua  |>  
  select(mh_phq_1, mh_phq_2, mh_phq_3, mh_phq_4, mh_phq_5, 
         mh_phq_6, mh_phq_7, mh_phq_8, mh_phq_9)

gad_items <- 
  ds_ua  |>  
  select(mh_gad_1, mh_gad_2, mh_gad_3, mh_gad_4, mh_gad_5, 
         mh_gad_6, mh_gad_7)

# Run

phq_alpha <- psych::alpha(phq_items)


gad_alpha <- psych::alpha(gad_items)


# table

reliability_table <- 
  tibble(
    Scale = c("PHQ-9", "GAD-7"),
    Items = c(9, 7),
    # We extract the Alpha once so we can use it in the calculations below
    Alpha = c(phq_alpha$total$raw_alpha, gad_alpha$total$raw_alpha),
    Lower_CI = Alpha - (1.96 * c(phq_alpha$total$ase, gad_alpha$total$ase)),
    Upper_CI = Alpha + (1.96 * c(phq_alpha$total$ase, gad_alpha$total$ase))
    ) |>
  mutate(across(where(is.numeric), \(x) round(x, 2))) |> 
  gt() |> 
  cols_label(
    Lower_CI = "Lower 95% CI",
    Upper_CI = "Upper 95% CI" 
  )

reliability_table

gtsave(reliability_table, "out/tables/ukr_cronbach.docx")

```

# Missing values

```{r miss-vals-through}
var_names_orig <- names(ds_ua)

names(ds_ua) <- paste0("Item ", seq_along(ds_ua))

var_names <-
  ds_ua |> 
  select(1:91) |> 
  select(-c("Item 1", 
            "Item 2", 
            "Item 3", 
            "Item 4",
            "Item 5",
            "Item 6",
            "Item 7",
            "Item 8",
            "Item 9",
            "Item 10",
            "Item 11",
            "Item 12",
            "Item 13",
            "Item 20",
            "Item 21",
            "Item 24",
            "Item 26",
            "Item 27",
            "Item 31",
            "Item 62")) |>
  colnames()
  

miss_through_plot <- 
  ds_ua |> 
  select(1:91) |> 
  select(-c("Item 1", 
            "Item 2", 
            "Item 3", 
            "Item 4",
            "Item 5",
            "Item 6",
            "Item 7",
            "Item 8",
            "Item 9",
            "Item 10",
            "Item 11",
            "Item 12",
            "Item 13",
            "Item 20",
            "Item 21",
            "Item 24",
            "Item 26",
            "Item 27",
            "Item 31",
            "Item 62")) |>  
  mutate(
    across(
      everything(),
      ~ as.character(.)
    )
  ) |>
  pivot_longer(
    everything(), 
    names_to = "variable", 
    values_to = "value"
    ) |>  
  mutate(missing = if_else(
    is.na(value), 
    "Missing", 
    "Present")) |> 
  count(variable, missing) |> 
  group_by(variable) |>
  mutate(prop = n / sum(n),
         variable = factor(variable, levels = var_names)) |> 
  filter(missing == "Missing") |>  
  ggplot(aes(x = variable, 
             y = prop)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.25)) +
  scale_fill_grey(start = 0.8, end = 0.2, name = "Data") +
  theme_minimal() +
  labs(x = "Variable", 
       y = "Percent") +
  theme(
    axis.text.x = element_text(angle = 45,
                               hjust = 1,
                               size = 10),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    axis.text.y = element_text(size = 10)
    )


miss_through_plot


ggsave(filename = "missing_vals_through.pdf",
       plot = miss_through_plot,
       path = "out/plots/",
       width = 210,
       height = 170,
       units = "mm",
       dpi = 320,
       scale = 1.5
       )


names(ds_ua) <- var_names_orig


rm(var_names, var_names_orig)
```
